### 2025-01-12 example_paper.tex
icaml_

%%%%%%%% ICML 2025 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2025} with \usepackage[nohyperref]{icml2025} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
% \usepackage{icml2025}

% If accepted, instead use the following line for the camera-ready submission:
\usepackage[accepted]{icml2025}

% For theorems and such
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}

% if you use cleveref..
\usepackage[capitalize,noabbrev]{cleveref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THEOREMS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% Todonotes is useful during development; simply uncomment the next line
%    and comment out the line below the next line to turn off comments
%\usepackage[disable,textsize=tiny]{todonotes}
\usepackage[textsize=tiny]{todonotes}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{OTCE: Hybrid SSM and Attention with Cross Domain Mixture of Experts to construct Observer-Thinker-Conceiver-Expresser for ICML 2025}

\begin{document}

\twocolumn[
\icmltitle{OTCE: Hybrid SSM and Attention with Cross Domain Mixture of Experts to construct Observer-Thinker-Conceiver-Expresser}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2025
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Firstname1 Lastname1}{equal,yyy}
\icmlauthor{Firstname2 Lastname2}{equal,yyy,comp}
\icmlauthor{Firstname3 Lastname3}{comp}
\icmlauthor{Firstname4 Lastname4}{sch}
\icmlauthor{Firstname5 Lastname5}{yyy}
\icmlauthor{Firstname6 Lastname6}{sch,yyy,comp}
\icmlauthor{Firstname7 Lastname7}{comp}
%\icmlauthor{}{sch}
\icmlauthor{Firstname8 Lastname8}{sch}
\icmlauthor{Firstname8 Lastname8}{yyy,comp}
%\icmlauthor{}{sch}
%\icmlauthor{}{sch}
\end{icmlauthorlist}

\icmlaffiliation{yyy}{Department of XXX, University of YYY, Location, Country}
\icmlaffiliation{comp}{Company Name, Location, Country}
\icmlaffiliation{sch}{School of ZZZ, Institute of WWW, Location, Country}

\icmlcorrespondingauthor{Firstname1 Lastname1}{first1.last1@xxx.edu}
\icmlcorrespondingauthor{Firstname2 Lastname2}{first2.last2@www.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

\begin{abstract}
We have found that combining Mamba with Transformer architecture outperforms using Mamba or Transformer architecture alone in language modeling tasks. We propose a position information injection method that connects the selective state space model with the quadratic attention, and integrates these two architectures with hybrid experts with cross-sharing domains, so that we can enjoy the advantages of both. We design a new architecture with a more biomimetic idea: Observer-Thinker-Conceiver-Expresser (OTCE), which can compete with well-known medium-scale open-source language models on a small scale in language modeling tasks.
\end{abstract}

\section{Introduction}
\label{submission}

The Transformers (Attention is All You Need~\cite{transformer2017}) architecture is popular in modern deep learning language modeling, which can directly capture the relationship between any two elements in a sequence, effectively handle long-distance dependencies, however, the architecture has two main drawbacks. First, when processing long sequences, its self-attention mechanism's quadratic complexity and cache size limit the ability to handle long contexts. Second, Transformer lacks a single summary state, which means that each generated token must compute over the entire context, which exacerbates the model's computational burden.
Meanwhile, the Selective State Model (Mamba~\cite{gu2023mamba}) has emerged. Mamba achieves linear scaling of sequence length during training and maintains a constant state size during generation through its selective state update mechanism. Moreover, due to its linear recursive state update mechanism, Mamba has a single summary state. However, Mamba also has a major drawback, that is, its positional information depends on the implicit local positional information provided by the causal convolution, while long-distance dependencies depend on the matrix D that skips the connection between input and output. This makes Mamba perform poorly in capturing long-distance dependencies, such as correctly capturing input-output formats in context learning (ICL).
An efficient model must have a small state, and an effective model must have a state that contains all the necessary information from the context. To build a model that is both efficient and effective, the key is to design a state that is both compact and comprehensive in capturing the necessary context information. Our main goal is to combine self-attention and the Selective State Model to overcome their respective limitations, further combine them with a mixed expert with extensive general and cross-domain knowledge to build a better basic model architecture than Transformers or Mamba. The model has the ability to learn long context dependencies, aggregate states, and efficient reasoning. This paper proposes a bionic perspective, aiming to explore new model architectures by cleverly combining the Selective State Model with self-attention mechanism. This approach can fully utilize the advantages of the two mechanisms and promote language modeling in a more efficient and effective direction.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except that
author information (names and affiliations) should be given. See
\cref{final author} for formatting instructions.

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{42}^{nd}$ International Conference on Machine Learning},
Vancouver, Canada, PMLR 267, 2025.
Copyright 2025 by the author(s).''

For those using the \textbf{\LaTeX} style file, this change (and others) is
handled automatically by simply changing
$\mathtt{\backslash usepackage\{icml2025\}}$ to
$$\mathtt{\backslash usepackage[accepted]\{icml2025\}}$$
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one. The running title consists of a
single line centered above a horizontal rule which is $1$~point thick.
The running head should be centered, bold and in $9$~point type. The
rule should be $10$~points above the main text. For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the \texttt{fancyhdr} package which is included in the ICML
2025 style file package. In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\icmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the specified format.

\subsection{Dimensions}

The text of the paper should be formatted in two columns, with an
overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
between the columns. The left margin should be 0.75~inches and the top
margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.
Do not write anything on the margins.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times typeface throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

ICML uses double-blind review, so author information must not appear. If
you are using \LaTeX\/ and the \texttt{icml2025.sty} file, use
\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
will not be printed unless \texttt{accepted} is passed as an argument to the
style file.
Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If you are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we
have shown \ldots'').

Do not anonymize citations in the reference section. The only exception are manuscripts that are
not yet published (e.g., under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have
to be submitted
as Supplementary Material via OpenReview\@. However, keep in mind that an ICML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look at the Supplementary Material when writing their
review (they are not required to look at more than the first $8$ pages of the submitted document).

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches below the
bottom rule surrounding the title. The authors' names should appear in 10~point
bold type, in a row, separated by white space, and centered. Author names should
not be broken across lines. Unbolded superscripted numbers, starting 1, should
be used to refer to affiliations.

Affiliations should be numbered in the order of appearance. A single footnote
block of text should be used to list all the affiliations. (Academic
affiliations should list Department, University, City, State/Region, Country.
Similarly for industrial affiliations.)

Each distinct affiliations should be listed once. If an author has multiple
affiliations, multiple superscripts should be placed after the name, separated
by thin spaces. If the authors would like to highlight equal contribution by
multiple first authors, those authors should have an asterisk placed after their
name in superscript, and the term ``\textsuperscript{*}Equal contribution"
should be placed in the footnote block ahead of the list of affiliations. A
list of corresponding authors and their emails (in the format Full Name
\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
Ideally only one or two names should be listed.

A sample file with author names is included in the ICML2025 style file
package. Turn on the \texttt{[accepted]} option to the stylefile to
see the names rendered. All of the guidelines above are implemented
by the \LaTeX\ style file.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below the final
address. The heading `Abstract' should be centered, bold, and in 11~point type.
The abstract body should use 10~point type, with a vertical spacing of
11~points, and should be indented 0.25~inches more than normal on left-hand and
right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
sentences. Gross violations will require correction at the camera-ready phase.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}
Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{Footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper.
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
\caption{Historical locations and number of accepted papers for International
Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
produced, the number of accepted papers for ICML 2008 was unknown and instead
estimated.}
\label{icml-historical}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{Figures}

You may want to include figures in the paper to illustrate
your approach and results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
\emph{after} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it, as in
\cref{icml-historical}. The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left. You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment \texttt{figure*} in \LaTeX). Always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
environments to format pseudocode. These require
the corresponding stylefiles, algorithm.sty and
algorithmic.sty, which are supplied with this package.
\cref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$}
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like
figures, these should be centered, legible, and numbered consecutively.
However, place the title \emph{above} the table with at least
0.1~inches of space before the title and the same after it, as in
\cref{sample-table}. The table title should be set in 9~point
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

\subsection{Theorems and such}
The preferred way is to number definitions, propositions, lemmas, etc. consecutively, within sections, as shown below.
\begin{definition}
\label{def:inj}
A function $f:X \to Y$ is injective if for any $x,y\in X$ different, $f(x)\ne f(y)$.
\end{definition}
Using \cref{def:inj} we immediate get the following result:
\begin{proposition}
If $f$ is injective mapping a set $X$ to another set $Y$, 
the cardinality of $Y$ is at least as large as that of $X$
\end{proposition}
\begin{proof} 
Left as an exercise to the reader. 
\end{proof}
\cref{lem:usefullemma} stated next will prove to be useful.
\begin{lemma}
\label{lem:usefullemma}
For any $f:X \to Y$ and $g:Y\to Z$ injective functions, $f \circ g$ is injective.
\end{lemma}
\begin{theorem}
\label{thm:bigtheorem}
If $f:X\to Y$ is bijective, the cardinality of $X$ and $Y$ are the same.
\end{theorem}
An easy corollary of \cref{thm:bigtheorem} is the following:
\begin{corollary}
If $f:X\to Y$ is bijective, 
the cardinality of $X$ is at least as large as that of $Y$.
\end{corollary}
\begin{assumption}
The set $X$ is finite.
\label{ass:xfinite}
\end{assumption}
\begin{remark}
According to some, it is only the finite case (cf. \cref{ass:xfinite}) that is interesting.
\end{remark}
%restatable

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{icml2025.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to \cref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent, e.g. use the actual current name of authors.
If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

\section*{Accessibility}
Authors are kindly asked to make their submissions as accessible as possible for everyone including people with disabilities and sensory or neurological differences.
Tips of how to achieve this and what to pay attention to will be provided on the conference website \url{http://icml.cc/}.

\section*{Software and Data}

If a paper is accepted, we strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate. This can be
done by including a URL in the camera-ready copy. However, \textbf{do not}
include URLs that reveal your institution or identity in your
submission for review. Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the OpenReview reviewing
system. Note that reviewers are not required to look at this material
when writing their review.

% Acknowledgements should only appear in the accepted version.
\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
usually should) include acknowledgements.  Such acknowledgements
should be placed at the end of the section, in an unnumbered section
that does not count towards the paper page limit. Typically, this will 
include thanks to reviewers who gave useful comments, to colleagues 
who contributed to the ideas, and to funding agencies and corporate 
sponsors that provided financial support.

\section*{Impact Statement}

Authors are \textbf{required} to include a statement of the potential 
broader impact of their work, including its ethical aspects and future 
societal consequences. This statement should be in an unnumbered 
section at the end of the paper (co-located with Acknowledgements -- 
the two may appear in either order, but both must be before References), 
and does not count toward the paper page limit. In many cases, where 
the ethical impacts and expected societal implications are those that 
are well established when advancing the field of Machine Learning, 
substantial discussion is not required, and a simple statement such 
as the following will suffice:

``This paper presents work whose goal is to advance the field of 
Machine Learning. There are many potential societal consequences 
of our work, none which we feel must be specifically highlighted here.''

The above statement can be used verbatim in such cases, but we 
encourage authors to think about whether there is content which does 
warrant further discussion, as this statement will be apparent if the 
paper is later flagged for ethics review.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2025}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\onecolumn
\section{You \emph{can} have an appendix here.}

You can have as much text here as you want. The main body must be at most $8$ pages long.
For the final version, one more page can be added.
If you want, you can use an appendix like this one.

The $\mathtt{\backslash onecolumn}$ command above can be kept in place if you prefer a one-column appendix, or can be removed if you prefer a two-column appendix.  Apart from this possible change, the style (font size, spacing, margins, page numbering, etc.) should be kept the same as the main body.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018, and modified by Alexandre Bouchard in
% 2019 and 2021 and by Csaba Szepesvari, Gang Niu and Sivan Sabato in 2022.
% Modified again in 2023 and 2024 by Sivan Sabato and Jonathan Scarlett.
% Previous contributors include Dan Roy, Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2025-01-12 paper.tex
icaml_

--- 2025-01-12 example_paper.tex
@@
 \begin{icmlauthorlist}
-\icmlauthor{Firstname1 Lastname1}{equal,yyy}
-\icmlauthor{Firstname2 Lastname2}{equal,yyy,comp}
-\icmlauthor{Firstname3 Lastname3}{comp}
-\icmlauthor{Firstname4 Lastname4}{sch}
-\icmlauthor{Firstname5 Lastname5}{yyy}
-\icmlauthor{Firstname6 Lastname6}{sch,yyy,comp}
-\icmlauthor{Firstname7 Lastname7}{comp}
-%\icmlauthor{}{sch}
-\icmlauthor{Firstname8 Lastname8}{sch}
-\icmlauthor{Firstname8 Lastname8}{yyy,comp}
+\icmlauthor{Jingze Shi}{equal,yyy}
+\icmlauthor{Bingheng Wu}{equal,yyy,comp}
+\icmlauthor{Ting Xie}{comp}
+\icmlauthor{Chunjun Zheng}{sch}
+
 %\icmlauthor{}{sch}
@@
 
-\subsection{Submitting Final Camera-Ready Copy}
+\subsection{Positional Information}
 
-The final versions of papers accepted for publication should follow the
-same format and naming convention as initial submissions, except that
-author information (names and affiliations) should be given. See
-\cref{final author} for formatting instructions.
+We first identified a key challenge in combining the Selective State Model with self-attention: the effective integration of positional information.
+In Mamba, positional information is provided by the implicit local positional information from the causal convolution, while self-attention itself cannot provide positional information, it relies on positional encoding to provide global positional context.
+To address this issue, we designed a relative positional information injection method that connects the inner product state of the Selective State Space with the inner product state of self-attention, allowing the input gate-state-output gate of the Selective State Space to make filtered relevant information have discrete relative positional information, and in self-attention, the discrete relative positional information is re-continuous to build long-term dependency relationships of relevant information.
+This method not only enables our model to have the ability to selectively process input sequences but also effectively capture long-distance dependency relationships.
+In complex multi-query associative recall tasks, our model trained on the same dataset outperforms larger-scale Mamba, Transformer models, and models that mix Mamba and Transformer without our proposed relative positional information injection method.
 
-The footnote, ``Preliminary work. Under review by the International
-Conference on Machine Learning (ICML). Do not distribute.'' must be
-modified to ``\textit{Proceedings of the
-$\mathit{42}^{nd}$ International Conference on Machine Learning},
-Vancouver, Canada, PMLR 267, 2025.
-Copyright 2025 by the author(s).''
+\subsection{Cross-Domain Mixture of Experts}
+In human society, knowledge is widely distributed across different domains, and these domains are interconnected through common foundational knowledge and cross-domain connections.
+To simulate this phenomenon in the model, we designed two types of cross-domain mixed experts: Cohesive Cross-Domain Expert and Expansive Cross-Domain Expert.
+These experts (multi-layer perceptrons) store and transfer common foundational knowledge and cross-domain knowledge between different domains by sharing parameters.
+The Cohesive Cross-Domain Expert achieves close integration between domains by sharing linear layer parameters within all experts, which is more suitable for small-scale models with fewer experts because of its faster computation speed.
+The Expansive Cross-Domain Expert shares a complete MLP parameter, adding a common domain knowledge gate in each expert to control the flow of common domain knowledge into private MLP parameters, which is more suitable for large-scale models with more experts because it allows for more flexible adjustment and utilization of common knowledge.
+Experimental results show that the performance of these two cross-domain mixed experts on the same dataset is better than shared expert isolated mixed experts, confirming the effectiveness of our design in promoting cross-domain knowledge transfer and improving model generalization.
 
-For those using the \textbf{\LaTeX} style file, this change (and others) is
-handled automatically by simply changing
-$\mathtt{\backslash usepackage\{icml2025\}}$ to
-$$\mathtt{\backslash usepackage[accepted]\{icml2025\}}$$
-Authors using \textbf{Word} must edit the
-footnote on the first page of the document themselves.
+\subsection{Architecture Design}
 
-Camera-ready copies should have the title of the paper as running head
-on each page except the first one. The running title consists of a
-single line centered above a horizontal rule which is $1$~point thick.
-The running head should be centered, bold and in $9$~point type. The
-rule should be $10$~points above the main text. For those using the
-\textbf{\LaTeX} style file, the original title is automatically set as running
-head using the \texttt{fancyhdr} package which is included in the ICML
-2025 style file package. In case that the original title exceeds the
-size restrictions, a shorter form can be supplied by using
+From a biological perspective, the relationship between input and output can be described by observing, thinking, conceiving, and expressing four stages.
+Inspired by this idea, we designed a new architecture with a bionic perspective: Observer-Thinker-Conceiver-Expresser (\textbf{OTCE}).
+The OTCE architecture mimics the natural process of information processing in biology, aiming to optimize information processing and transmission in a modular way.
+In the Observer module, we use the selective state space's selection ability to filter out irrelevant information in the sequence to retain relevant information.
+In the Thinker module, we use the self-attention's ability to capture dependencies between any two elements in a sequence of any length, regardless of their position in the sequence, to build long-term dependency relationships.
+In the Conceiver module, we use the linear recursive state update mechanism of the state space to build a single summary state information.
+In the Expresser module, we combine the context-aware state information produced by self-attention considering all elements with the summary state information to build a context-aware summary state.
+We also studied the combination of the Selective State Space and self-attention with ordinary multi-layer perceptrons and cross-domain mixed experts, and finally determined a model combination with the lowest perplexity at the same parameter scale.
 
-\verb|\icmltitlerunning{...}|
+We empirically validated OTCE on multiple tasks, including semantic similarity evaluation, long-short text classification, natural language inference, keyword recognition, different domain selection tasks, context learning, and multi-query associative recall tasks.
+These experiments demonstrate the effectiveness of the OTCE architecture in handling complex language tasks.
 
-just before $\mathtt{\backslash begin\{document\}}$.
-Authors using \textbf{Word} must edit the header of the document themselves.
-
-\section{Format of the Paper}
-
-All submissions must follow the specified format.
-
-\subsection{Dimensions}
-
-The text of the paper should be formatted in two columns, with an
-overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
-between the columns. The left margin should be 0.75~inches and the top
-margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
-whether you print on US letter or A4 paper, but all final versions
-must be produced for US letter size.
-Do not write anything on the margins.
-
-The paper body should be set in 10~point type with a vertical spacing
-of 11~points. Please use Times typeface throughout the text.
-
-\subsection{Title}
-
-The paper title should be set in 14~point bold type and centered
-between two horizontal rules that are 1~point thick, with 1.0~inch
-between the top rule and the top edge of the page. Capitalize the
-first letter of content words and put the rest of the title in lower
-case.
-
-\subsection{Author Information for Submission}
-\label{author info}
-
-ICML uses double-blind review, so author information must not appear. If
-you are using \LaTeX\/ and the \texttt{icml2025.sty} file, use
-\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
-will not be printed unless \texttt{accepted} is passed as an argument to the
-style file.
-Submissions that include the author information will not
-be reviewed.
-
-\subsubsection{Self-Citations}
-
-If you are citing published papers for which you are an author, refer
-to yourself in the third person. In particular, do not use phrases
-that reveal your identity (e.g., ``in previous work \cite{langley00}, we
-have shown \ldots'').
-
-Do not anonymize citations in the reference section. The only exception are manuscripts that are
-not yet published (e.g., under submission). If you choose to refer to
-such unpublished manuscripts \cite{anonymous}, anonymized copies have
-to be submitted
-as Supplementary Material via OpenReview\@. However, keep in mind that an ICML
-paper should be self contained and should contain sufficient detail
-for the reviewers to evaluate the work. In particular, reviewers are
-not required to look at the Supplementary Material when writing their
-review (they are not required to look at more than the first $8$ pages of the submitted document).
-
-\subsubsection{Camera-Ready Author Information}
-\label{final author}
-
-If a paper is accepted, a final camera-ready copy must be prepared.
-%
-For camera-ready papers, author information should start 0.3~inches below the
-bottom rule surrounding the title. The authors' names should appear in 10~point
-bold type, in a row, separated by white space, and centered. Author names should
-not be broken across lines. Unbolded superscripted numbers, starting 1, should
-be used to refer to affiliations.
-
-Affiliations should be numbered in the order of appearance. A single footnote
-block of text should be used to list all the affiliations. (Academic
-affiliations should list Department, University, City, State/Region, Country.
-Similarly for industrial affiliations.)
-
-Each distinct affiliations should be listed once. If an author has multiple
-affiliations, multiple superscripts should be placed after the name, separated
-by thin spaces. If the authors would like to highlight equal contribution by
-multiple first authors, those authors should have an asterisk placed after their
-name in superscript, and the term ``\textsuperscript{*}Equal contribution"
-should be placed in the footnote block ahead of the list of affiliations. A
-list of corresponding authors and their emails (in the format Full Name
-\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
-Ideally only one or two names should be listed.
-
-A sample file with author names is included in the ICML2025 style file
-package. Turn on the \texttt{[accepted]} option to the stylefile to
-see the names rendered. All of the guidelines above are implemented
-by the \LaTeX\ style file.
-
-\subsection{Abstract}
-
-The paper abstract should begin in the left column, 0.4~inches below the final
-address. The heading `Abstract' should be centered, bold, and in 11~point type.
-The abstract body should use 10~point type, with a vertical spacing of
-11~points, and should be indented 0.25~inches more than normal on left-hand and
-right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
-abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
-sentences. Gross violations will require correction at the camera-ready phase.
-
-\subsection{Partitioning the Text}
-
-You should organize your paper into sections and paragraphs to help
-readers place a structure on the material and understand its
-contributions.
-
-\subsubsection{Sections and Subsections}
-
-Section headings should be numbered, flush left, and set in 11~pt bold
-type with the content words capitalized. Leave 0.25~inches of space
-before the heading and 0.15~inches after the heading.
-
-Similarly, subsection headings should be numbered, flush left, and set
-in 10~pt bold type with the content words capitalized. Leave
-0.2~inches of space before the heading and 0.13~inches afterward.
-
-Finally, subsubsection headings should be numbered, flush left, and
-set in 10~pt small caps with the content words capitalized. Leave
-0.18~inches of space before the heading and 0.1~inches after the
-heading.
-
-Please use no more than three levels of headings.
-
-\subsubsection{Paragraphs and Footnotes}
-Within each section or subsection, you should further partition the
-paper into paragraphs. Do not indent the first line of a given
-paragraph, but insert a blank line between succeeding ones.
-
-You can use footnotes\footnote{Footnotes
-should be complete sentences.} to provide readers with additional
-information about a topic without interrupting the flow of the paper.
-Indicate footnotes with a number in the text where the point is most
-relevant. Place the footnote in 9~point type at the bottom of the
-column in which it appears. Precede the first footnote in a column
-with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
-appear in each column, in the same order as they appear in the text,
-but spread them across columns and pages if possible.}
-
-\begin{figure}[ht]
-\vskip 0.2in
-\begin{center}
-\centerline{\includegraphics[width=\columnwidth]{icml_numpapers}}
-\caption{Historical locations and number of accepted papers for International
-Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
-Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
-produced, the number of accepted papers for ICML 2008 was unknown and instead
-estimated.}
-\label{icml-historical}
-\end{center}
-\vskip -0.2in
+\begin{figure}[H]
+   \centering
+   \includegraphics[width=1.0\linewidth]{fig/otce.png}
+   \caption{(\textbf{OTCE Architecture}.) OTCE demonstrates the overall combined architecture and process of using Observer, Thinker, Conceiver, and Expresser modules in language modeling tasks.
+Observer, Thinker, Conceiver, and Expresser show their internal combination of selective state space, self-attention, multi-layer perceptron, and cross-domain mixed experts.}
+   \label{fig:otce}
 \end{figure}
 
-\subsection{Figures}
+\section{Background}
+\subsection{Selective State Space Models}
 
-You may want to include figures in the paper to illustrate
-your approach and results. Such artwork should be centered,
-legible, and separated from the text. Lines should be dark and at
-least 0.5~points thick for purposes of reproduction, and text should
-not appear on a gray background.
+Selective state space models~\cite{gu2023mamba} consider that a fundamental problem in sequence modeling is to compress the context into a smaller state.
+From this perspective, the attention mechanism of Transformers explicitly stores the entire context information, as if reviewing all previous inputs and generated tokens before writing each token.
+In contrast, RNNs only refer to a fixed number of previous tokens each time, which allows for faster writing but may forget key tokens.
 
-Label all distinct components of each figure. If the figure takes the
-form of a graph, then give a name for each axis and include a legend
-that briefly describes each curve. Do not include a title inside the
-figure; instead, the caption should serve this function.
-
-Number figures sequentially, placing the figure number and caption
-\emph{after} the graphics, with at least 0.1~inches of space before
-the caption and 0.1~inches after it, as in
-\cref{icml-historical}. The figure caption should be set in
-9~point type and centered unless it runs two or more lines, in which
-case it should be flush left. You may float figures to the top or
-bottom of a column, and you may set wide figures across both columns
-(use the environment \texttt{figure*} in \LaTeX). Always place
-two-column figures at the top or bottom of the page.
-
-\subsection{Algorithms}
-
-If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
-environments to format pseudocode. These require
-the corresponding stylefiles, algorithm.sty and
-algorithmic.sty, which are supplied with this package.
-\cref{alg:example} shows an example.
-
-\begin{algorithm}[tb]
-   \caption{Bubble Sort}
-   \label{alg:example}
-\begin{algorithmic}
-   \STATE {\bfseries Input:} data $x_i$, size $m$
-   \REPEAT
-   \STATE Initialize $noChange = true$.
-   \FOR{$i=1$ {\bfseries to} $m-1$}
-   \IF{$x_i > x_{i+1}$}
-   \STATE Swap $x_i$ and $x_{i+1}$
-   \STATE $noChange = false$
-   \ENDIF
-   \ENDFOR
-   \UNTIL{$noChange$ is $true$}
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Tables}
-
-You may also want to include tables that summarize material. Like
-figures, these should be centered, legible, and numbered consecutively.
-However, place the title \emph{above} the table with at least
-0.1~inches of space before the title and the same after it, as in
-\cref{sample-table}. The table title should be set in 9~point
-type and centered unless it runs two or more lines, in which case it
-should be flush left.
+In the precursor state space models of selective state space models, there are 4 parameters$(\Delta t, A, B, C)$, and they do not change with the input.
+These parameters control the following two stages:
 
@@
 
-\bibliography{example_paper}
+\bibliography{paper}
 \bibliographystyle{icml2025}

### 2025-01-16 paper.tex
fist check
11

@@
 \usepackage[capitalize,noabbrev]{cleveref}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{xcolor}
+\usepackage{booktabs}
 
@@
 These parameters control the following two stages:
+\begin{align}
+   h'(t) &= Ah(t) + Bx(t) \quad \text{(1a)} \nonumber \\
+   y(t) &= Ch(t) \quad \text{(1b)} \nonumber \\
+   h_t &= \overline{A}h_{t-1} + \overline{B}x_t \quad \text{(2a)} \nonumber \\
+   y_t &= Ch_t \quad \text{(2b)} \nonumber \\
+   \overline{K} &= (C\overline{B}, C\overline{A}\overline{B}, \ldots, C\overline{A}^{k-1}\overline{B}, \ldots) \quad \text{(3a)} \nonumber \\
+   y &= x * \overline{K} \quad \text{(3b)} \nonumber
+\end{align}
+\begin{itemize}
+   \item In the first stage (1a \& 1b), the continuous parameters $h'(t)$ are transformed into discrete parameters $h_t$ through a fixed formula $\overline{A} = f_A(\Delta t, A)$ and $\overline{B} = f_B(\Delta t, A, B)$, where $(f_A, f_B)$ is called the discretization rule.
+The most common is the zero-order hold (ZOH) rule, defined as $\overline{A} = \exp(\Delta t A)$ and $\overline{B} = (\Delta t A)^{-1} (\exp(\Delta t A) - I) \cdot \Delta t B$.
+   \item In the second stage (2a \& 2b and 3a \& 3b), after the parameters are transformed from $(\Delta t, A, B, C)$ to $(\overline{A}, \overline{B}, C)$, linear recursion or global convolution can be used for computation.
+\end{itemize}
+State space models cannot update states selectively based on different input information.
 
-% Note use of \abovespace and \belowspace to get reasonable spacing
-% above and below tabular lines.
-
-\begin{table}[t]
-\caption{Classification accuracies for naive Bayes and flexible
-Bayes on various data sets.}
-\label{sample-table}
-\vskip 0.15in
-\begin{center}
-\begin{small}
-\begin{sc}
-\begin{tabular}{lcccr}
-\toprule
-Data set & Naive & Flexible & Better? \\
-\midrule
-Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
-Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
-Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
-Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
-Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
-Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
-Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
-Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
-\bottomrule
-\end{tabular}
-\end{sc}
-\end{small}
-\end{center}
-\vskip -0.1in
-\end{table}
-
-Tables contain textual material, whereas figures contain graphical material.
-Specify the contents of each row and column in the table's topmost
-row. Again, you may float tables to a column's top or bottom, and set
-wide tables across both columns. Place two-column tables at the
-top or bottom of the page.
+The solution of selective state space models (Mamba~\citep{gu2023mamba}) is that, compared to state space models that compress all historical information, they design a simple selection mechanism that parameterizes the input of the state space model,making $(\Delta t, B, C)$  a function of the input.
 

### 2025-01-24 paper.tex
Updated Title and Abstract

--- 2025-01-12 paper.tex
@@
 \twocolumn[
-\icmltitle{OTCE: Hybrid SSM and Attention with Cross Domain Mixture of Experts to construct Observer-Thinker-Conceiver-Expresser}
+\icmltitle{Re-Examine Hybrid State-Space and Self-Attention for In-Context Learning}
 
@@
 \icmlauthor{Bingheng Wu}{equal,yyy,comp}
-\icmlauthor{Ting Xie}{comp}
-\icmlauthor{Chunjun Zheng}{sch}
 
@@
 \begin{abstract}
-We have found that combining Mamba with Transformer architecture outperforms using Mamba or Transformer architecture alone in language modeling tasks.
-We propose a position information injection method that connects the selective state space model with the quadratic attention, and integrates these two architectures with hybrid experts with cross-sharing domains, so that we can enjoy the advantages of both.
-We design a new architecture with a more biomimetic idea: Observer-Thinker-Conceiver-Expresser (OTCE), which can compete with well-known medium-scale open-source language models on a small scale in language modeling tasks.
+% 最近的研究表明, 将状态空间算法驱动的 Mamba 与自注意力算法驱动的 Transformer 相结合, 在大多数语言建模任务上的表现超越了单独使用 Mamba 或 Transformer. 
+% 但是, 目前主流的混合建模架构模型在情景学习任务上的表现并不理想, 我们重新审视了这两种算法的优势和劣势, 从原理出发对这种混合建模的结构重新设计. 
+% 最终, 重新设计的架构, 在标准短文本任务中提升了 1.3 \% 效果, 在自然长文本任务中提升了 20.86 \% 效果, 在合成长文本任务中提升了 27.06 \% 效果.
+Recent research has shown that combining the state-space algorithm-driven Mamba with the self-attention algorithm-driven Transformer outperforms using Mamba or Transformer alone in most language modeling tasks.
+However, the performance of the mainstream hybrid modeling architecture models in in-context learning tasks is not ideal.
+We re-examine the advantages and disadvantages of these two algorithms and redesign the structure of this hybrid modeling from the principle.
+The finally redesigned architecture improves the performance by 1.3\% in standard short text tasks, 20.86\% in natural long text tasks, and 27.06\% in synthetic long text tasks.
 \end{abstract}

### 2025-01-24 paper.tex
Updated Author list

--- 2025-01-24 paper.tex
@@
 
+% % For code
+% \usepackage{listings}
+% \usepackage[frozencache,cachedir=.]{minted}
+
 % if you use cleveref..
@@
 %\usepackage[disable,textsize=tiny]{todonotes}
-\usepackage[textsize=tiny]{todonotes}
+% \usepackage[textsize=tiny]{todonotes}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{OTCE: Hybrid SSM and Attention with Cross Domain Mixture of Experts to construct Observer-Thinker-Conceiver-Expresser for ICML 2025}
+\icmltitlerunning{Re-Examine Hybrid State-Space and Self-Attention for In-Context Learning}
 
@@
 \begin{icmlauthorlist}
-\icmlauthor{Jingze Shi}{equal,yyy}
-\icmlauthor{Bingheng Wu}{equal,yyy,comp}
-
-%\icmlauthor{}{sch}
-%\icmlauthor{}{sch}
+\icmlauthor{Jingze Shi}{equal,IR}
+\icmlauthor{Bingheng Wu}{equal,IR}
 \end{icmlauthorlist}
 
-\icmlaffiliation{yyy}{Department of XXX, University of YYY, Location, Country}
-\icmlaffiliation{comp}{Company Name, Location, Country}
-\icmlaffiliation{sch}{School of ZZZ, Institute of WWW, Location, Country}
+\icmlaffiliation{IR}{Independent Researcher}
 
-\icmlcorrespondingauthor{Firstname1 Lastname1}{first1.last1@xxx.edu}
-\icmlcorrespondingauthor{Firstname2 Lastname2}{first2.last2@www.uk}
+\icmlcorrespondingauthor{Jingze Shi}{losercheems@gmail.com}
+\icmlcorrespondingauthor{Bingheng Wu}{wubingheng52136@gmail.com}
 

### 2025-01-24 paper.tex
Update Introduction

--- 2025-01-24 paper.tex
@@
 \label{submission}
+% Transformers~\cite{transformer2017} 架构的自注意力算法能够直接捕捉序列中任意两个元素间的关系, 有效处理长距离依赖问题. 但是却受到二次复杂度的限制.
+% Mamba~\cite{gu2023mamba} 架构的状态空间算法能够在训练期间实现序列长度的线性缩放, 并在生成期间保持恒定的状态大小, 但是却在捕捉长距离依赖问题上导致偏差.
+% 混合建模架构模型, 例如 Wonderful Matrices~\cite{shi2024wonderfulmatrices}, Jamba~\cite{lieber2024jamba}, 等等, 使用状态空间和自注意力进行混合建模, 使模型具备与 Mamba 类似的效率和与 Transformer 类似的效果.
+然而, 这些模型在情景学习任务上的表现却与原始的 Transformer 相比, 仍然有不小的差距.
+The self-attention algorithm of the Transformers~\cite{wolf-etal-2020-transformers} architecture can directly capture the relationship between any two elements in a sequence, effectively handle long-distance dependencies.
+However, it is limited by quadratic complexity.
+The state-space algorithm of the Mamba~\cite{gu2023mamba} architecture can achieve linear scaling of sequence length during training and maintain a constant state size during generation, but it leads to bias in capturing long-distance dependencies.
+Hybrid modeling architecture models, such as Wonderful Matrices~\cite{shi2024wonderfulmatrices}, Jamba~\cite{lieber2024jamba}, etc., use state-space and self-attention for hybrid modeling, making the model have efficiency similar to The Mamba and effect similar to The Transformer.
+However, these models still have a significant gap in performance in in-context learning tasks compared to the original Transformer.
 
-The Transformers (Attention is All You Need~\cite{transformer2017}) architecture is popular in modern deep learning language modeling, which can directly capture the relationship between any two elements in a sequence, effectively handle long-distance dependencies, however, the architecture has two main drawbacks.
-First, when processing long sequences, its self-attention mechanism's quadratic complexity and cache size limit the ability to handle long contexts.
-Second, Transformer lacks a single summary state, which means that each generated token must compute over the entire context, which exacerbates the model's computational burden.
-Meanwhile, the Selective State Model (Mamba~\cite{gu2023mamba}) has emerged.
-Mamba achieves linear scaling of sequence length during training and maintains a constant state size during generation through its selective state update mechanism.
-Moreover, due to its linear recursive state update mechanism, Mamba has a single summary state.
-However, Mamba also has a major drawback, that is, its positional information depends on the implicit local positional information provided by the causal convolution, while long-distance dependencies depend on the matrix D that skips the connection between input and output.
-This makes Mamba perform poorly in capturing long-distance dependencies, such as correctly capturing input-output formats in context learning (ICL).
-An efficient model must have a small state, and an effective model must have a state that contains all the necessary information from the context.
-To build a model that is both efficient and effective, the key is to design a state that is both compact and comprehensive in capturing the necessary context information.
-Our main goal is to combine self-attention and the Selective State Model to overcome their respective limitations, further combine them with a mixed expert with extensive general and cross-domain knowledge to build a better basic model architecture than Transformers or Mamba.
-The model has the ability to learn long context dependencies, aggregate states, and efficient reasoning.
-This paper proposes a bionic perspective, aiming to explore new model architectures by cleverly combining the Selective State Model with self-attention mechanism.
-This approach can fully utilize the advantages of the two mechanisms and promote language modeling in a more efficient and effective direction.
+% 我们提出了 Self-Attention before LM-Head~\ref{fig:architecture}, 这是对现有的混合堆叠架构模型的一种简单改变, 将状态空间和自注意力修改为使用相同的位置编码, 并在 LM-Head 预测概率分布之前使用自注意力和前馈网络构成的 Transformer 块.
+这种方法使得模型能够继续利用状态空间的高效上下文摘要和自注意力有效联想召回的优势, 而不会在最终的token预测上产生偏差.
+We propose Self-Attention before LM-Head~\ref{fig:architecture}, which is a simple change to the existing hybrid stacked architecture models, modifying the state-space and self-attention to use the same positional encoding, and using a Transformer block composed of self-attention and feed-forward networks before the LM-Head predicts the probability distribution.
+This method allows the model to continue to leverage the advantages of the efficient context summary of the state-space and the effective associative recall of self-attention without bias in the final token prediction.
 
-\subsection{Positional Information}
+% 我们的研究与评估表明, Self-Attention before LM-Head 只需要很少的结构与参数调整, 就能够与基线混合模型相比, 在上下文学习任务基准上取得更好的性能.
+例如, 在标准短文本任务中, 我们的模型提升了 1.3 \% 的效果, 在自然长文本任务中提升了 20.86 \% 的效果, 在合成长文本任务中提升了 27.06 \% 的效果, 并且在大海捞针任务上取得了最先进的效果.
+Our research and evaluation show that Self-Attention before LM-Head can achieve better performance on the in-context learning task benchmark compared to the baseline hybrid model with only a few structural and parameter adjustments.
+For example, in standard short text tasks, our model improves performance by 1.3\%, in natural long text tasks by 20.86\%, in synthetic long text tasks by 27.06\%, and achieves state-of-the-art performance on the needle in a haystack task.
 
-We first identified a key challenge in combining the Selective State Model with self-attention: the effective integration of positional information.
-In Mamba, positional information is provided by the implicit local positional information from the causal convolution, while self-attention itself cannot provide positional information, it relies on positional encoding to provide global positional context.
-To address this issue, we designed a relative positional information injection method that connects the inner product state of the Selective State Space with the inner product state of self-attention, allowing the input gate-state-output gate of the Selective State Space to make filtered relevant information have discrete relative positional information, and in self-attention, the discrete relative positional information is re-continuous to build long-term dependency relationships of relevant information.
-This method not only enables our model to have the ability to selectively process input sequences but also effectively capture long-distance dependency relationships.
-In complex multi-query associative recall tasks, our model trained on the same dataset outperforms larger-scale Mamba, Transformer models, and models that mix Mamba and Transformer without our proposed relative positional information injection method.
+\begin{figure*}[ht]
+   \centering
+   \includegraphics[width=\linewidth]{fig/architecture.pdf}
+   \caption{
+      % 状态空间和自注意力都使用相同的位置编码, 并且在 LM-Head 之前使用自注意力和前馈网络构成的 Transformer 块, 无论模型骨干的其他部分如何组合.
+     \textbf{Self-Attention before LM-Head}.
+      The state-space and self-attention both use the same positional encoding, and a Transformer block composed of self-attention and feed-forward networks is used before the LM-Head, regardless of how the other parts of the model backbone are combined.
+   }
+   \label{fig:architecture}
+\end{figure*}
 
-\subsection{Cross-Domain Mixture of Experts}
-In human society, knowledge is widely distributed across different domains, and these domains are interconnected through common foundational knowledge and cross-domain connections.
-To simulate this phenomenon in the model, we designed two types of cross-domain mixed experts: Cohesive Cross-Domain Expert and Expansive Cross-Domain Expert.
-These experts (multi-layer perceptrons) store and transfer common foundational knowledge and cross-domain knowledge between different domains by sharing parameters.
-The Cohesive Cross-Domain Expert achieves close integration between domains by sharing linear layer parameters within all experts, which is more suitable for small-scale models with fewer experts because of its faster computation speed.
-The Expansive Cross-Domain Expert shares a complete MLP parameter, adding a common domain knowledge gate in each expert to control the flow of common domain knowledge into private MLP parameters, which is more suitable for large-scale models with more experts because it allows for more flexible adjustment and utilization of common knowledge.
-Experimental results show that the performance of these two cross-domain mixed experts on the same dataset is better than shared expert isolated mixed experts, confirming the effectiveness of our design in promoting cross-domain knowledge transfer and improving model generalization.
+% \section{Background}
+% \subsection{Selective State Space Models}
 
-\subsection{Architecture Design}
-
-From a biological perspective, the relationship between input and output can be described by observing, thinking, conceiving, and expressing four stages.
-Inspired by this idea, we designed a new architecture with a bionic perspective: Observer-Thinker-Conceiver-Expresser (\textbf{OTCE}).
-The OTCE architecture mimics the natural process of information processing in biology, aiming to optimize information processing and transmission in a modular way.
-In the Observer module, we use the selective state space's selection ability to filter out irrelevant information in the sequence to retain relevant information.
-In the Thinker module, we use the self-attention's ability to capture dependencies between any two elements in a sequence of any length, regardless of their position in the sequence, to build long-term dependency relationships.
-In the Conceiver module, we use the linear recursive state update mechanism of the state space to build a single summary state information.
-In the Expresser module, we combine the context-aware state information produced by self-attention considering all elements with the summary state information to build a context-aware summary state.
-We also studied the combination of the Selective State Space and self-attention with ordinary multi-layer perceptrons and cross-domain mixed experts, and finally determined a model combination with the lowest perplexity at the same parameter scale.
-
-We empirically validated OTCE on multiple tasks, including semantic similarity evaluation, long-short text classification, natural language inference, keyword recognition, different domain selection tasks, context learning, and multi-query associative recall tasks.
-These experiments demonstrate the effectiveness of the OTCE architecture in handling complex language tasks.
-
-\begin{figure}[H]
-   \centering
-   \includegraphics[width=1.0\linewidth]{fig/otce.png}
-   \caption{(\textbf{OTCE Architecture}.) OTCE demonstrates the overall combined architecture and process of using Observer, Thinker, Conceiver, and Expresser modules in language modeling tasks.
-Observer, Thinker, Conceiver, and Expresser show their internal combination of selective state space, self-attention, multi-layer perceptron, and cross-domain mixed experts.}
-   \label{fig:otce}
-\end{figure}
-
-\section{Background}
-\subsection{Selective State Space Models}
-
-Selective state space models~\cite{gu2023mamba} consider that a fundamental problem in sequence modeling is to compress the context into a smaller state.
+% Selective state space models~\cite{gu2023mamba} consider that a fundamental problem in sequence modeling is to compress the context into a smaller state.
 From this perspective, the attention mechanism of Transformers explicitly stores the entire context information, as if reviewing all previous inputs and generated tokens before writing each token.
@@
 
-In the precursor state space models of selective state space models, there are 4 parameters$(\Delta t, A, B, C)$, and they do not change with the input.
+% In the precursor state space models of selective state space models, there are 4 parameters$(\Delta t, A, B, C)$, and they do not change with the input.
 These parameters control the following two stages:
+% \begin{align}
+%    h'(t) &= Ah(t) + Bx(t) \quad \text{(1a)} \nonumber \\
+%    y(t) &= Ch(t) \quad \text{(1b)} \nonumber \\
+%    h_t &= \overline{A}h_{t-1} + \overline{B}x_t \quad \text{(2a)} \nonumber \\
+%    y_t &= Ch_t \quad \text{(2b)} \nonumber \\
+%    \overline{K} &= (C\overline{B}, C\overline{A}\overline{B}, \ldots, C\overline{A}^{k-1}\overline{B}, \ldots) \quad \text{(3a)} \nonumber \\
+%    y &= x * \overline{K} \quad \text{(3b)} \nonumber
+% \end{align}
+% \begin{itemize}
+%    \item In the first stage (1a \& 1b), the continuous parameters $h'(t)$ are transformed into discrete parameters $h_t$ through a fixed formula $\overline{A} = f_A(\Delta t, A)$ and $\overline{B} = f_B(\Delta t, A, B)$, where $(f_A, f_B)$ is called the discretization rule.
+The most common is the zero-order hold (ZOH) rule, defined as $\overline{A} = \exp(\Delta t A)$ and $\overline{B} = (\Delta t A)^{-1} (\exp(\Delta t A) - I) \cdot \Delta t B$.
+%    \item In the second stage (2a \& 2b and 3a \& 3b), after the parameters are transformed from $(\Delta t, A, B, C)$ to $(\overline{A}, \overline{B}, C)$, linear recursion or global convolution can be used for computation.
+% \end{itemize}
+% State space models cannot update states selectively based on different input information.
 
-% Note use of \abovespace and \belowspace to get reasonable spacing
-% above and below tabular lines.
+% The solution of selective state space models (Mamba~\citep{gu2023mamba}) is that, compared to state space models that compress all historical information, they design a simple selection mechanism that parameterizes the input of the state space model,making $(\Delta t, B, C)$  a function of the input.
 
-\begin{table}[t]
-\caption{Classification accuracies for naive Bayes and flexible
-Bayes on various data sets.}
-\label{sample-table}
-\vskip 0.15in
-\begin{center}
-\begin{small}
-\begin{sc}
-\begin{tabular}{lcccr}
-\toprule
-Data set & Naive & Flexible & Better? \\
-\midrule
-Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
-Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
-Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
-Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
-Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
-Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
-Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
-Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
-\bottomrule
-\end{tabular}
-\end{sc}
-\end{small}
-\end{center}
-\vskip -0.1in
-\end{table}
+% \subsection{Theorems and such}
+% The preferred way is to number definitions, propositions, lemmas, etc. consecutively, within sections, as shown below.
+% \begin{definition}
+% \label{def:inj}
+% A function $f:X \to Y$ is injective if for any $x,y\in X$ different, $f(x)\ne f(y)$.
+% \end{definition}
+% Using \cref{def:inj} we immediate get the following result:
+% \begin{proposition}
+% If $f$ is injective mapping a set $X$ to another set $Y$, 
+% the cardinality of $Y$ is at least as large as that of $X$
+% \end{proposition}
+% \begin{proof} 
+% Left as an exercise to the reader. 
+% \end{proof}
+% \cref{lem:usefullemma} stated next will prove to be useful.
+% \begin{lemma}
+% \label{lem:usefullemma}
+% For any $f:X \to Y$ and $g:Y\to Z$ injective functions, $f \circ g$ is injective.
+% \end{lemma}
+% \begin{theorem}
+% \label{thm:bigtheorem}
+% If $f:X\to Y$ is bijective, the cardinality of $X$ and $Y$ are the same.
+% \end{theorem}
+% An easy corollary of \cref{thm:bigtheorem} is the following:
+% \begin{corollary}
+% If $f:X\to Y$ is bijective, 
+% the cardinality of $X$ is at least as large as that of $Y$.
+% \end{corollary}
+% \begin{assumption}
+% The set $X$ is finite.
+% \label{ass:xfinite}
+% \end{assumption}
+% \begin{remark}
+% According to some, it is only the finite case (cf. \cref{ass:xfinite}) that is interesting.
+% \end{remark}
+% %restatable
 
-Tables contain textual material, whereas figures contain graphical material.
-Specify the contents of each row and column in the table's topmost
-row. Again, you may float tables to a column's top or bottom, and set
-wide tables across both columns. Place two-column tables at the
-top or bottom of the page.
+% \subsection{Citations and References}
 
-\subsection{Theorems and such}
-The preferred way is to number definitions, propositions, lemmas, etc. consecutively, within sections, as shown below.
-\begin{definition}
-\label{def:inj}
-A function $f:X \to Y$ is injective if for any $x,y\in X$ different, $f(x)\ne f(y)$.
-\end{definition}
-Using \cref{def:inj} we immediate get the following result:
-\begin{proposition}
-If $f$ is injective mapping a set $X$ to another set $Y$, 
-the cardinality of $Y$ is at least as large as that of $X$
-\end{proposition}
-\begin{proof} 
-Left as an exercise to the reader. 
-\end{proof}
-\cref{lem:usefullemma} stated next will prove to be useful.
-\begin{lemma}
-\label{lem:usefullemma}
-For any $f:X \to Y$ and $g:Y\to Z$ injective functions, $f \circ g$ is injective.
-\end{lemma}
-\begin{theorem}
-\label{thm:bigtheorem}
-If $f:X\to Y$ is bijective, the cardinality of $X$ and $Y$ are the same.
-\end{theorem}
-An easy corollary of \cref{thm:bigtheorem} is the following:
-\begin{corollary}
-If $f:X\to Y$ is bijective, 
-the cardinality of $X$ is at least as large as that of $Y$.
-\end{corollary}
-\begin{assumption}
-The set $X$ is finite.
-\label{ass:xfinite}
-\end{assumption}
-\begin{remark}
-According to some, it is only the finite case (cf. \cref{ass:xfinite}) that is interesting.
-\end{remark}
-%restatable
+% Please use APA reference format regardless of your formatter
+% or word processor. If you rely on the \LaTeX\/ bibliographic
+% facility, use \texttt{natbib.sty} and \texttt{icml2025.bst}
+% included in the style-file package to obtain this format.
 
-\subsection{Citations and References}
+% Citations within the text should include the authors' last names and
+% year. If the authors' names are included in the sentence, place only
+% the year in parentheses, for example when referencing Arthur Samuel's
+% pioneering work \yrcite{Samuel59}. Otherwise place the entire
+% reference in parentheses with the authors and year separated by a
+% comma \cite{Samuel59}. List multiple references separated by
+% semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
+% construct only for citations with three or more authors or after
+% listing all authors to a publication in an earlier reference \cite{MachineLearningI}.
 
-Please use APA reference format regardless of your formatter
-or word processor. If you rely on the \LaTeX\/ bibliographic
-facility, use \texttt{natbib.sty} and \texttt{icml2025.bst}
-included in the style-file package to obtain this format.
+% Authors should cite their own work in the third person
+% in the initial version of their paper submitted for blind review.
+% Please refer to \cref{author info} for detailed instructions on how to
+% cite your own papers.
 
-Citations within the text should include the authors' last names and
-year. If the authors' names are included in the sentence, place only
-the year in parentheses, for example when referencing Arthur Samuel's
-pioneering work \yrcite{Samuel59}. Otherwise place the entire
-reference in parentheses with the authors and year separated by a
-comma \cite{Samuel59}. List multiple references separated by
-semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
-construct only for citations with three or more authors or after
-listing all authors to a publication in an earlier reference \cite{MachineLearningI}.
+% Use an unnumbered first-level section heading for the references, and use a
+% hanging indent style, with the first line of the reference flush against the
+% left margin and subsequent lines indented by 10 points. The references at the
+% end of this document give examples for journal articles \cite{Samuel59},
+% conference publications \cite{langley00}, book chapters \cite{Newell81}, books
+% \cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
+% \cite{mitchell80}, and dissertations \cite{kearns89}.
 
-Authors should cite their own work in the third person
-in the initial version of their paper submitted for blind review.
-Please refer to \cref{author info} for detailed instructions on how to
-cite your own papers.
+% Alphabetize references by the surnames of the first authors, with
+% single author entries preceding multiple author entries. Order
+% references for the same authors by year of publication, with the
+% earliest first. Make sure that each reference includes all relevant
+% information (e.g., page numbers).
 
-Use an unnumbered first-level section heading for the references, and use a
-hanging indent style, with the first line of the reference flush against the
-left margin and subsequent lines indented by 10 points. The references at the
-end of this document give examples for journal articles \cite{Samuel59},
-conference publications \cite{langley00}, book chapters \cite{Newell81}, books
-\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
-\cite{mitchell80}, and dissertations \cite{kearns89}.
+% Please put some effort into making references complete, presentable, and
+% consistent, e.g. use the actual current name of authors.
+% If using bibtex, please protect capital letters of names and
+% abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
+% in your .bib file.
 
-Alphabetize references by the surnames of the first authors, with
-single author entries preceding multiple author entries. Order
-references for the same authors by year of publication, with the
-earliest first. Make sure that each reference includes all relevant
-information (e.g., page numbers).
+% \section*{Accessibility}
+% Authors are kindly asked to make their submissions as accessible as possible for everyone including people with disabilities and sensory or neurological differences.
+% Tips of how to achieve this and what to pay attention to will be provided on the conference website \url{http://icml.cc/}.
 
-Please put some effort into making references complete, presentable, and
-consistent, e.g. use the actual current name of authors.
-If using bibtex, please protect capital letters of names and
-abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
-in your .bib file.
+% \section*{Software and Data}
 
-\section*{Accessibility}
-Authors are kindly asked to make their submissions as accessible as possible for everyone including people with disabilities and sensory or neurological differences.
-Tips of how to achieve this and what to pay attention to will be provided on the conference website \url{http://icml.cc/}.
+% If a paper is accepted, we strongly encourage the publication of software and data with the
+% camera-ready version of the paper whenever appropriate. This can be
+% done by including a URL in the camera-ready copy. However, \textbf{do not}
+% include URLs that reveal your institution or identity in your
+% submission for review. Instead, provide an anonymous URL or upload
+% the material as ``Supplementary Material'' into the OpenReview reviewing
+% system. Note that reviewers are not required to look at this material
+% when writing their review.
 
-\section*{Software and Data}
+% % Acknowledgements should only appear in the accepted version.
+% \section*{Acknowledgements}
 
-If a paper is accepted, we strongly encourage the publication of software and data with the
-camera-ready version of the paper whenever appropriate. This can be
-done by including a URL in the camera-ready copy. However, \textbf{do not}
-include URLs that reveal your institution or identity in your
-submission for review. Instead, provide an anonymous URL or upload
-the material as ``Supplementary Material'' into the OpenReview reviewing
-system. Note that reviewers are not required to look at this material
-when writing their review.
+% \textbf{Do not} include acknowledgements in the initial version of
+% the paper submitted for blind review.
 
-% Acknowledgements should only appear in the accepted version.
-\section*{Acknowledgements}
+% If a paper is accepted, the final camera-ready version can (and
+% usually should) include acknowledgements.  Such acknowledgements
+% should be placed at the end of the section, in an unnumbered section
+% that does not count towards the paper page limit. Typically, this will 
+% include thanks to reviewers who gave useful comments, to colleagues 
+% who contributed to the ideas, and to funding agencies and corporate 
+% sponsors that provided financial support.
 
-\textbf{Do not} include acknowledgements in the initial version of
-the paper submitted for blind review.
+% \section*{Impact Statement}
 
-If a paper is accepted, the final camera-ready version can (and
-usually should) include acknowledgements.  Such acknowledgements
-should be placed at the end of the section, in an unnumbered section
-that does not count towards the paper page limit. Typically, this will 
-include thanks to reviewers who gave useful comments, to colleagues 
-who contributed to the ideas, and to funding agencies and corporate 
-sponsors that provided financial support.
+% Authors are \textbf{required} to include a statement of the potential 
+% broader impact of their work, including its ethical aspects and future 
+% societal consequences. This statement should be in an unnumbered 
+% section at the end of the paper (co-located with Acknowledgements -- 
+% the two may appear in either order, but both must be before References), 
+% and does not count toward the paper page limit. In many cases, where 
+% the ethical impacts and expected societal implications are those that 
+% are well established when advancing the field of Machine Learning, 
+% substantial discussion is not required, and a simple statement such 
+% as the following will suffice:
 
-\section*{Impact Statement}
+% ``This paper presents work whose goal is to advance the field of 
+% Machine Learning. There are many potential societal consequences 
+% of our work, none which we feel must be specifically highlighted here.''
 
-Authors are \textbf{required} to include a statement of the potential 
-broader impact of their work, including its ethical aspects and future 
-societal consequences. This statement should be in an unnumbered 
-section at the end of the paper (co-located with Acknowledgements -- 
-the two may appear in either order, but both must be before References), 
-and does not count toward the paper page limit. In many cases, where 
-the ethical impacts and expected societal implications are those that 
-are well established when advancing the field of Machine Learning, 
-substantial discussion is not required, and a simple statement such 
-as the following will suffice:
-
-``This paper presents work whose goal is to advance the field of 
-Machine Learning. There are many potential societal consequences 
-of our work, none which we feel must be specifically highlighted here.''
-
-The above statement can be used verbatim in such cases, but we 
-encourage authors to think about whether there is content which does 
-warrant further discussion, as this statement will be apparent if the 
-paper is later flagged for ethics review.
+% The above statement can be used verbatim in such cases, but we 
+% encourage authors to think about whether there is content which does 
+% warrant further discussion, as this statement will be apparent if the 
+% paper is later flagged for ethics review.
 
@@
 % references without citing it in the main text, use \nocite
-\nocite{langley00}
+% \nocite{langley00}
 

### 2025-01-26 paper.tex
add introduction

@@
       }
+      \textbf{}
+
    \label{fig:architecture}
@@
 
-% \section{Background}
-% \subsection{Selective State Space Models}
+\section{Background}
+\subsection{Selective State Space Models}
 
-% Selective state space models~\cite{gu2023mamba} consider that a fundamental problem in sequence modeling is to compress the context into a smaller state.
-From this perspective, the attention mechanism of Transformers explicitly stores the entire context information, as if reviewing all previous inputs and generated tokens before writing each token.
-In contrast, RNNs only refer to a fixed number of previous tokens each time, which allows for faster writing but may forget key tokens.
+% 在自然语言处理（NLP）领域，SSM被用于建模文本序列的动态特性。其优势在于能够高效地处理长序列数据，并通过状态变量的更新机制捕捉序列中的时间依赖性。然而，传统的SSM存在一些局限性，例如线性时不变（LTI）系统的矩阵参数（如A、B、C）在整个序列生成过程中保持固定，这使得模型难以进行内容感知的推理。例如，在处理需要选择性关注或忽略特定输入的任务时，传统SSM的表现不如基于自注意力机制的Transformer模型。
+In the field of natural language processing (NLP), SSM is used to model the dynamic characteristics of text sequences.
+Its advantage is that it can efficiently handle long sequence data and capture the time dependency in the sequence through the update mechanism of the state variables.
+However, traditional SSM has some limitations, such as the matrix parameters (such as A, B, C) of the linear time-invariant (LTI) system remain fixed throughout the entire sequence generation process, making it difficult for the model to perform content-aware reasoning.
+For example, when dealing with tasks that require selective attention or ignoring specific inputs, the performance of traditional SSM is not as good as the Transformer model based on the self-attention mechanism.
 
-% In the precursor state space models of selective state space models, there are 4 parameters$(\Delta t, A, B, C)$, and they do not change with the input.
-These parameters control the following two stages:
-% \begin{align}
-%    h'(t) &= Ah(t) + Bx(t) \quad \text{(1a)} \nonumber \\
-%    y(t) &= Ch(t) \quad \text{(1b)} \nonumber \\
-%    h_t &= \overline{A}h_{t-1} + \overline{B}x_t \quad \text{(2a)} \nonumber \\
-%    y_t &= Ch_t \quad \text{(2b)} \nonumber \\
-%    \overline{K} &= (C\overline{B}, C\overline{A}\overline{B}, \ldots, C\overline{A}^{k-1}\overline{B}, \ldots) \quad \text{(3a)} \nonumber \\
-%    y &= x * \overline{K} \quad \text{(3b)} \nonumber
-% \end{align}
-% \begin{itemize}
-%    \item In the first stage (1a \& 1b), the continuous parameters $h'(t)$ are transformed into discrete parameters $h_t$ through a fixed formula $\overline{A} = f_A(\Delta t, A)$ and $\overline{B} = f_B(\Delta t, A, B)$, where $(f_A, f_B)$ is called the discretization rule.
-The most common is the zero-order hold (ZOH) rule, defined as $\overline{A} = \exp(\Delta t A)$ and $\overline{B} = (\Delta t A)^{-1} (\exp(\Delta t A) - I) \cdot \Delta t B$.
-%    \item In the second stage (2a \& 2b and 3a \& 3b), after the parameters are transformed from $(\Delta t, A, B, C)$ to $(\overline{A}, \overline{B}, C)$, linear recursion or global convolution can be used for computation.
-% \end{itemize}
-% State space models cannot update states selectively based on different input information.
+\noindent
+\begin{minipage}{0.48\textwidth}
+\small
+\begin{align}
+   h'(t) &= A h(t) + B x(t) \\
+   y(t) &= C h(t)
+\end{align}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\small
+\begin{align}
+   h'(t) &= A h(t) + B x(t) \\
+   y(t) &= C h(t)
+\end{align}
+\end{minipage}
 
-% The solution of selective state space models (Mamba~\citep{gu2023mamba}) is that, compared to state space models that compress all historical information, they design a simple selection mechanism that parameterizes the input of the state space model,making $(\Delta t, B, C)$  a function of the input.
+\noindent
+\begin{minipage}{0.48\textwidth}
+\small
+\begin{align}
+   h'(t) &= A h(t) + B x(t) \\
+   y(t) &= C h(t)
+\end{align}
+\end{minipage}
+\begin{minipage}{0.48\textwidth}
+\small
+\begin{align}
+   h'(t) &= A h(t) + B x(t) \\
+   y(t) &= C h(t)
+\end{align}
+\end{minipage}
+
+%为了克服这些局限性，研究者们提出了多种改进方法。例如，~\cite{mamba2}模型通过引入选择性扫描算法（Selective Scan）和硬件感知算法（Hardware-Aware Algorithm），使得SSM能够动态调整参数，从而更好地处理长序列数据并提高计算效率。这种改进的SSM，也被称为选择性状态空间模型（Selective SSM，简称S6），追求能够像Transformer一样构建高效的序列处理模块。但是即便如此，它仍然不如CNN 和 Transformer在计算上高效，而现代并行计算设备的发展使得这种计算效率的差距变得更加明显, 从而限制了SSM在更大规模的序列数据上的训练,因此揭示选择性SSM和注意力机制之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
+
+To overcome these limitations, researchers have proposed various improvement methods.
+For example, the Mamba~\cite{gu2023mamba} model introduces the Selective Scan algorithm and the Hardware-Aware Algorithm, allowing SSM to dynamically adjust parameters to better handle long sequence data and improve computational efficiency.
+This improved SSM, also known as Selective State Space Model (Selective SSM, abbreviated as S6), aims to build an efficient sequence processing module like Transformer.
+However, even so, it is still not as computationally efficient as CNN and Transformer, and the development of modern parallel computing devices makes this computational efficiency gap more pronounced, limiting the training of SSM on larger-scale sequence data.
+Therefore, it is very important to reveal a deeper relationship between Selective SSM and the attention mechanism and propose a new hybrid modeling architecture to overcome these limitations.
+
+\subsection{Attention and SSM}
+% 在Transformer模型中，自注意力机制通过计算查询（Query）、键（Key）和值（Value）之间的相似度来确定各个位置的重要性权重。具体来说，自注意力机制首先计算查询和键之间的点积，然后通过softmax函数将这些点积转换为注意力权重，最后将这些权重应用于值向量，以生成加权的上下文表示。
+In the Transformer model, the self-attention mechanism determines the importance weights of each position by calculating the similarity between queries, keys, and values.
+Specifically, the self-attention mechanism first calculates the dot product between the query and the key, then converts these dot products into attention weights through the softmax function, and finally applies these weights to the value vector to generate a weighted context representation.
+
+\subsection{Hybrid Modeling}
 

### 2025-01-26 paper.tex
Update method

@@
 
-% \subsection{Theorems and such}
-% The preferred way is to number definitions, propositions, lemmas, etc. consecutively, within sections, as shown below.
-% \begin{definition}
-% \label{def:inj}
-% A function $f:X \to Y$ is injective if for any $x,y\in X$ different, $f(x)\ne f(y)$.
-% \end{definition}
-% Using \cref{def:inj} we immediate get the following result:
-% \begin{proposition}
-% If $f$ is injective mapping a set $X$ to another set $Y$, 
-% the cardinality of $Y$ is at least as large as that of $X$
-% \end{proposition}
-% \begin{proof} 
-% Left as an exercise to the reader. 
-% \end{proof}
-% \cref{lem:usefullemma} stated next will prove to be useful.
-% \begin{lemma}
-% \label{lem:usefullemma}
-% For any $f:X \to Y$ and $g:Y\to Z$ injective functions, $f \circ g$ is injective.
-% \end{lemma}
-% \begin{theorem}
-% \label{thm:bigtheorem}
-% If $f:X\to Y$ is bijective, the cardinality of $X$ and $Y$ are the same.
-% \end{theorem}
-% An easy corollary of \cref{thm:bigtheorem} is the following:
-% \begin{corollary}
-% If $f:X\to Y$ is bijective, 
-% the cardinality of $X$ is at least as large as that of $Y$.
-% \end{corollary}
-% \begin{assumption}
-% The set $X$ is finite.
-% \label{ass:xfinite}
-% \end{assumption}
-% \begin{remark}
-% According to some, it is only the finite case (cf. \cref{ass:xfinite}) that is interesting.
-% \end{remark}
-% %restatable
+\section{Method}
 
-% \subsection{Citations and References}
+% 以往的混合建模架构模型, 是使用Mamba~\cite{gu2023mamba}块中的一维卷积来隐式进行位置编码, 而删除了自注意力使用的旋转位置编码.
+而旋转位置编码并不直接对注意力分数矩阵进行操作, 为了良好的外推性能, 我们可以将其添加到状态空间.
+让我们回顾状态空间算法~\ref{}, 首先, 矩阵 $B$ 控制是否让输入 $x_t$ 进入状态 $h_t$, 我们在矩阵 $B$ 中加入旋转位置编码, 矩阵 $B$ 作为输入门对 $x_t$ 筛选后使 $h_t$ 具备了绝对位置信息, 然后, 矩阵 $A$ 控制是否让状态 $h_{t-1}$ 进入状态 $h_t$, 也就是说它也允许过去状态的绝对位置信息影响到当前状态, 最后, 矩阵 $C$ 控制是否让状态 $h_t$ 进入输出 $y_t$, 我们在矩阵 $C$ 中加入旋转位置编码, 矩阵 $C$ 作为输出门对 $h_t$ 筛选后使 $y_t$ 具备了相对位置信息.
+但值得注意的是, 由于状态空间的递归性质, 即只保留一个状态的缓存, 位置编码会受到叠加态的影响, 即使原始的一维卷积位置编码也是如此, 这也是它难以进行上下文学习的缺陷.
+所以直接使用经过状态空间处理的位置信息, 作为自注意力的位置编码, 难免会导致位置信息的混乱.
+为了解决这个问题, 我们应该保留自注意力的旋转位置编码, 重新为自注意力提供原始的位置信息.
+In the past hybrid modeling architecture models, a one-dimensional convolution in the Mamba~\cite{gu2023mamba} block is used to implicitly perform positional encoding, while the rotational positional encoding used by self-attention is removed.
+The rotational positional encoding does not directly operate on the attention score matrix.
+For good extrapolation performance, we can add it to the state space.
+Let's review the state-space algorithm~\ref{}, first, the matrix $B$ controls whether to let the input $x_t$ enter the state $h_t$, we add rotational positional encoding to the matrix $B$, the matrix $B$ as an input gate filters $x_t$ after $h_t$ has absolute positional information, then, the matrix $A$ controls whether to let the state $h_{t-1}$ enter the state $h_t$, that is, it also allows the absolute positional information of the past state to affect the current state, finally, the matrix $C$ controls whether to let the state $h_t$ enter the output $y_t$, we add rotational positional encoding to the matrix $C$, the matrix $C$ as an output gate filters $h_t$ after $y_t$ has relative positional information.
+However, it is worth noting that due to the recursive nature of the state space, that is, only one state cache is retained, the positional encoding will be affected by the superposition state, even the original one-dimensional convolution positional encoding is the same, which is also its difficulty in context learning defect.
+So using the position information processed by the state space directly as the positional encoding of self-attention will inevitably lead to the confusion of position information.
+To solve this problem, we should retain the rotational positional encoding of self-attention and provide the original position information for self-attention.
 
-% Please use APA reference format regardless of your formatter
-% or word processor. If you rely on the \LaTeX\/ bibliographic
-% facility, use \texttt{natbib.sty} and \texttt{icml2025.bst}
-% included in the style-file package to obtain this format.
-
-% Citations within the text should include the authors' last names and
-% year. If the authors' names are included in the sentence, place only
-% the year in parentheses, for example when referencing Arthur Samuel's
-% pioneering work \yrcite{Samuel59}. Otherwise place the entire
-% reference in parentheses with the authors and year separated by a
-% comma \cite{Samuel59}. List multiple references separated by
-% semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
-% construct only for citations with three or more authors or after
-% listing all authors to a publication in an earlier reference \cite{MachineLearningI}.
-
-% Authors should cite their own work in the third person
-% in the initial version of their paper submitted for blind review.
-% Please refer to \cref{author info} for detailed instructions on how to
-% cite your own papers.
-
-% Use an unnumbered first-level section heading for the references, and use a
-% hanging indent style, with the first line of the reference flush against the
-% left margin and subsequent lines indented by 10 points. The references at the
-% end of this document give examples for journal articles \cite{Samuel59},
-% conference publications \cite{langley00}, book chapters \cite{Newell81}, books
-% \cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
-% \cite{mitchell80}, and dissertations \cite{kearns89}.
-
-% Alphabetize references by the surnames of the first authors, with
-% single author entries preceding multiple author entries. Order
-% references for the same authors by year of publication, with the
-% earliest first. Make sure that each reference includes all relevant
-% information (e.g., page numbers).
-
-% Please put some effort into making references complete, presentable, and
-% consistent, e.g. use the actual current name of authors.
-% If using bibtex, please protect capital letters of names and
-% abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
-% in your .bib file.
-
-% \section*{Accessibility}
-% Authors are kindly asked to make their submissions as accessible as possible for everyone including people with disabilities and sensory or neurological differences.
-% Tips of how to achieve this and what to pay attention to will be provided on the conference website \url{http://icml.cc/}.
-
-% \section*{Software and Data}
-
-% If a paper is accepted, we strongly encourage the publication of software and data with the
-% camera-ready version of the paper whenever appropriate. This can be
-% done by including a URL in the camera-ready copy. However, \textbf{do not}
-% include URLs that reveal your institution or identity in your
-% submission for review. Instead, provide an anonymous URL or upload
-% the material as ``Supplementary Material'' into the OpenReview reviewing
-% system. Note that reviewers are not required to look at this material
-% when writing their review.
-
-% % Acknowledgements should only appear in the accepted version.
-% \section*{Acknowledgements}
-
-% \textbf{Do not} include acknowledgements in the initial version of
-% the paper submitted for blind review.
-
-% If a paper is accepted, the final camera-ready version can (and
-% usually should) include acknowledgements.  Such acknowledgements
-% should be placed at the end of the section, in an unnumbered section
-% that does not count towards the paper page limit. Typically, this will 
-% include thanks to reviewers who gave useful comments, to colleagues 
-% who contributed to the ideas, and to funding agencies and corporate 
-% sponsors that provided financial support.
-
-% \section*{Impact Statement}
-
-% Authors are \textbf{required} to include a statement of the potential 
-% broader impact of their work, including its ethical aspects and future 
-% societal consequences. This statement should be in an unnumbered 
-% section at the end of the paper (co-located with Acknowledgements -- 
-% the two may appear in either order, but both must be before References), 
-% and does not count toward the paper page limit. In many cases, where 
-% the ethical impacts and expected societal implications are those that 
-% are well established when advancing the field of Machine Learning, 
-% substantial discussion is not required, and a simple statement such 
-% as the following will suffice:
-
-% ``This paper presents work whose goal is to advance the field of 
-% Machine Learning. There are many potential societal consequences 
-% of our work, none which we feel must be specifically highlighted here.''
-
-% The above statement can be used verbatim in such cases, but we 
-% encourage authors to think about whether there is content which does 
-% warrant further discussion, as this statement will be apparent if the 
-% paper is later flagged for ethics review.
-
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-% \nocite{langley00}
+% 状态空间的计算量随着序列长度 $T$ 呈线性增长的特性这里不再赘述, 其数据依赖化的相关参数可以使模型具备信息的选择性处理能力, 线性递归赋予的聚合状态可以让我们只计算last token.
+当然, 通过函数逼近产生状态矩阵 $A$ 的最优解来记住历史的方式, 只能精确捕捉到 $h_{t-1}$ 到 $h_t$ 的状态变化, 而逐渐衰减旧的状态信息, 这就导致了在需要强大的复制能力或上下文学习能力或长上下文推理能力的任务上, 在预测 token 之前, 状态空间的信息摘要会产生偏差.
+为了解决这个问题, 我们应该在 LM-Head 之前使用没有压缩上下文信息, 可以不受距离限制对元素加权而产生上下文感知状态的自注意力和前馈网络构成的 Transformer 块, 使模型能够继续利用状态空间的高效上下文摘要和自注意力有效联想召回的优势, 而不会在最终的token预测上产生偏差.
+The computational complexity of the state space grows linearly with the sequence length $T$, and its data-dependent related parameters can enable the model to have the ability to selectively process information.
+The linear recursion gives the aggregated state that allows us to calculate only the last token.
+Of course, by approximating the function to generate the optimal solution of the state matrix $A$ to remember history, it can only accurately capture the state change from $h_{t-1}$ to $h_t$ and gradually decay the old state information, which leads to the need for strong replication, context learning, or long-context reasoning capabilities.
+In tasks that require powerful capabilities, before predicting the token, the information summary of the state space will produce bias.
+To solve this problem, we should use self-attention and feed-forward networks that do not compress context information before the LM-Head, which can produce context-aware states by weighting elements without distance restrictions, allowing the model to continue to leverage the efficient context summary of the state space and the effective associative recall of self-attention without bias in the final token prediction.
 

### 2025-01-26 paper.tex
change introduction

--- 2025-01-26 paper.tex
@@
 For example, when dealing with tasks that require selective attention or ignoring specific inputs, the performance of traditional SSM is not as good as the Transformer model based on the self-attention mechanism.
+      % 状态空间模型是一种用于描述系统动态行为的数学模型，其基本形式为：
+      State-space models are mathematical models used to describe the dynamic behavior of systems, and their basic form is:
+      \begin{minipage}{0.45\textwidth}
+         \begin{alignat}{2}
+            h'(t) &= Ah(t) + Bx(t) && \tag{1a} \\
+            y(t) &= Ch(t) + Dx(t) && \tag{1b}
+         \end{alignat}
+         %其中，h(t) 是状态向量，x(t) 是输入向量，y(t) 是输出向量，A、B、C、D 是系统矩阵 
+         %翻译
+         where $h(t)$ is the state vector, $x(t)$ is the input vector, $y(t)$ is the output vector, and $A$, $B$, $C$, $D$ are system matrices.
 
-\noindent
-\begin{minipage}{0.48\textwidth}
-\small
-\begin{align}
-   h'(t) &= A h(t) + B x(t) \\
-   y(t) &= C h(t)
-\end{align}
          \end{minipage}
-\begin{minipage}{0.48\textwidth}
-\small
-\begin{align}
-   h'(t) &= A h(t) + B x(t) \\
-   y(t) &= C h(t)
-\end{align}
+         \hfill
+         \begin{minipage}{0.45\textwidth}
+         \begin{alignat}{2}
+            h_t &= \overline{A}h_{t-1} + \overline{B}x_t && \tag{2a} \\
+            y_t &= Ch_t && \tag{2b}
+         % 从连续时间系统的状态空间模型出发，可以通过离散化方法得到离散时间的状态更新公式,方程 (2a) 和 (2b) 代表状态空间模型的离散化形式。它们描述了在离散时间间隔内，状态向量和输出向量如何基于前一个状态和当前输入进行更新。
+        \end{alignat}
+         Starting from the state-space model of continuous-time systems, the discrete-time state update formula can be obtained through discretization methods.
+Equations (2a) and (2b) represent the discrete form of the state-space model.
+They describe how the state vector and output vector are updated based on the previous state and current input at discrete time intervals.
+
          \end{minipage}
+         \begin{minipage}{0.45\textwidth}
+         \begin{alignat}{2}
+            \overline{K} &= (C\overline{B}, CAB, \ldots, C\overline{A}^k\overline{B}, \ldots) && \tag{3a} \\
+            y &= x * \overline{K} && \tag{3b}
+         \end{alignat}
+         \end{minipage}
+         % 以上为
 
-\noindent
-\begin{minipage}{0.48\textwidth}
-\small
-\begin{align}
-   h'(t) &= A h(t) + B x(t) \\
-   y(t) &= C h(t)
-\end{align}
-\end{minipage}
-\begin{minipage}{0.48\textwidth}
-\small
-\begin{align}
-   h'(t) &= A h(t) + B x(t) \\
-   y(t) &= C h(t)
-\end{align}
-\end{minipage}
+%以上为SSM-S4的过程，所有结构化 SSM 都是 LTI 模型，LTI 模型存在基本的效率限制,为了克服这些局限性，研究者们提出了多种改进方法。例如，~\cite{mamba2}模型通过引入选择性扫描算法（Selective Scan）和硬件感知算法（Hardware-Aware Algorithm），使得SSM能够动态调整参数，从而更好地处理长序列数据并提高计算效率。这种改进的SSM，也被称为选择性状态空间模型（Selective SSM，简称S6），追求能够像Transformer一样构建高效的序列处理模块。但是即便如此，它仍然不如CNN 和 Transformer在计算上高效，而现代并行计算设备的发展使得这种计算效率的差距变得更加明显, 从而限制了SSM在更大规模的序列数据上的训练,因此揭示选择性SSM和注意力机制之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
 
-%为了克服这些局限性，研究者们提出了多种改进方法。例如，~\cite{mamba2}模型通过引入选择性扫描算法（Selective Scan）和硬件感知算法（Hardware-Aware Algorithm），使得SSM能够动态调整参数，从而更好地处理长序列数据并提高计算效率。这种改进的SSM，也被称为选择性状态空间模型（Selective SSM，简称S6），追求能够像Transformer一样构建高效的序列处理模块。但是即便如此，它仍然不如CNN 和 Transformer在计算上高效，而现代并行计算设备的发展使得这种计算效率的差距变得更加明显, 从而限制了SSM在更大规模的序列数据上的训练,因此揭示选择性SSM和注意力机制之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
-
+ The above is the process of SSM-S4.
+All structured SSMs are LTI models, and LTI models have basic efficiency limitations.
 To overcome these limitations, researchers have proposed various improvement methods.
-For example, the Mamba~\cite{gu2023mamba} model introduces the Selective Scan algorithm and the Hardware-Aware Algorithm, allowing SSM to dynamically adjust parameters to better handle long sequence data and improve computational efficiency.
-This improved SSM, also known as Selective State Space Model (Selective SSM, abbreviated as S6), aims to build an efficient sequence processing module like Transformer.
-However, even so, it is still not as computationally efficient as CNN and Transformer, and the development of modern parallel computing devices makes this computational efficiency gap more pronounced, limiting the training of SSM on larger-scale sequence data.
-Therefore, it is very important to reveal a deeper relationship between Selective SSM and the attention mechanism and propose a new hybrid modeling architecture to overcome these limitations.
+For example, the Mamba~\cite{mamba2} model introduces the Selective Scan algorithm and the Hardware-Aware Algorithm, allowing SSM to dynamically adjust parameters to better handle long sequence data and improve computational efficiency.
+This improved SSM, also known as Selective State Space Model (Selective SSM, referred to as S6), aims to build efficient sequence processing modules like Transformer.
+However, even so, it is still not as efficient as CNN and Transformer in computation, and the development of modern parallel computing devices makes this computational efficiency gap more obvious, thereby limiting the training of SSM on larger-scale sequence data.
+Therefore, it is very important to reveal the deeper relationship between Selective SSM and the attention mechanism and propose a new hybrid modeling architecture to overcome these limitations.
 

### 2025-01-27 paper.tex

@@
 \section{Background}
-\subsection{Selective State Space Models}
+\subsection{State-Space}
 
-% 在自然语言处理（NLP）领域，SSM被用于建模文本序列的动态特性。其优势在于能够高效地处理长序列数据，并通过状态变量的更新机制捕捉序列中的时间依赖性。然而，传统的SSM存在一些局限性，例如线性时不变（LTI）系统的矩阵参数（如A、B、C）在整个序列生成过程中保持固定，这使得模型难以进行内容感知的推理。例如，在处理需要选择性关注或忽略特定输入的任务时，传统SSM的表现不如基于自注意力机制的Transformer模型。
+% 在自然语言处理（NLP）领域，SSM被用于建模文本序列的动态特性。其优势在于能够高效地处理长序列数据，并通过状态变量的更新机制捕捉序列中的时间依赖性。然而，传统的SSM存在一些局限性，例如线性时不变（LTI）系统的矩阵参数（如A、B、C）在整个序列生成过程中保持固定，这使得模型难以进行内容感知的推理。例如，在处理需要选择性关注或忽略特定输入的任务时，传统SSM的表现不如基于自注意力机制的Transformer模型。状态空间模型是一种用于描述系统动态行为的数学模型，其基本形式为：
 In the field of natural language processing (NLP), SSM is used to model the dynamic characteristics of text sequences.
@@
 For example, when dealing with tasks that require selective attention or ignoring specific inputs, the performance of traditional SSM is not as good as the Transformer model based on the self-attention mechanism.
-      % 状态空间模型是一种用于描述系统动态行为的数学模型，其基本形式为：
 State-space models are mathematical models used to describe the dynamic behavior of systems, and their basic form is:
-      \begin{minipage}{0.45\textwidth}
-         \begin{alignat}{2}
-            h'(t) &= Ah(t) + Bx(t) && \tag{1a} \\
-            y(t) &= Ch(t) + Dx(t) && \tag{1b}
-         \end{alignat}
+
+\begin{equation}
+\begin{aligned}
+   h'(t) &= Ah(t) + Bx(t) \\
+   y(t) &= Ch(t) + Dx(t)
+\end{aligned}
+\end{equation}
+
 %其中，h(t) 是状态向量，x(t) 是输入向量，y(t) 是输出向量，A、B、C、D 是系统矩阵 
-         %翻译
 where $h(t)$ is the state vector, $x(t)$ is the input vector, $y(t)$ is the output vector, and $A$, $B$, $C$, $D$ are system matrices.
 
-         \end{minipage}
-         \hfill
-         \begin{minipage}{0.45\textwidth}
-         \begin{alignat}{2}
-            h_t &= \overline{A}h_{t-1} + \overline{B}x_t && \tag{2a} \\
-            y_t &= Ch_t && \tag{2b}
-         % 从连续时间系统的状态空间模型出发，可以通过离散化方法得到离散时间的状态更新公式,方程 (2a) 和 (2b) 代表状态空间模型的离散化形式。它们描述了在离散时间间隔内，状态向量和输出向量如何基于前一个状态和当前输入进行更新。
-        \end{alignat}
+\begin{equation}
+\begin{aligned}
+   h_t &= Ah_{t-1} + Bx_t \\
+   y_t &= Ch_t
+\end{aligned}
+\end{equation}
+% \begin{alignat}{2}
+%    h_t &= \overline{A}h_{t-1} + \overline{B}x_t && \tag{2a} \\
+%    y_t &= Ch_t && \tag{2b}
+% % 从连续时间系统的状态空间模型出发，可以通过离散化方法得到离散时间的状态更新公式,方程 (2a) 和 (2b) 代表状态空间模型的离散化形式。它们描述了在离散时间间隔内，状态向量和输出向量如何基于前一个状态和当前输入进行更新。
+% \end{alignat}
 Starting from the state-space model of continuous-time systems, the discrete-time state update formula can be obtained through discretization methods.
@@
 
-         \end{minipage}
-         \begin{minipage}{0.45\textwidth}
-         \begin{alignat}{2}
-            \overline{K} &= (C\overline{B}, CAB, \ldots, C\overline{A}^k\overline{B}, \ldots) && \tag{3a} \\
-            y &= x * \overline{K} && \tag{3b}
-         \end{alignat}
-         \end{minipage}
-         % 以上为
+         % \end{minipage}
+%          \begin{minipage}{0.45\textwidth}
+%          \begin{alignat}{2}
+%             \overline{K} &= (C\overline{B}, CAB, \ldots, C\overline{A}^k\overline{B}, \ldots) && \tag{3a} \\
+%             y &= x * \overline{K} && \tag{3b}
+%          \end{alignat}
+%          \end{minipage}
+%          % 以上为
 

### 2025-01-28 paper.tex
edit background

@@
 
-\subsection{Attention and SSM}
+\subsection{Self Attention}
 % 在Transformer模型中，自注意力机制通过计算查询（Query）、键（Key）和值（Value）之间的相似度来确定各个位置的重要性权重。具体来说，自注意力机制首先计算查询和键之间的点积，然后通过softmax函数将这些点积转换为注意力权重，最后将这些权重应用于值向量，以生成加权的上下文表示。
@@
 
+\begin{equation}
+   \begin{aligned}
+      Y &= \operatorname*{softmax}({QK^\top}) \cdot V   \end{aligned}
+   \end{equation}
+
+% 通过自注意力机制，Transformer模型能够直接捕捉序列中任意两个元素之间的关系，从而有效处理长距离依赖问题。然而，自注意力机制的二次复杂度限制了Transformer模型的计算效率，使得其在处理长序列数据时表现不佳。为了克服这一局限性，研究者们提出了许多改进方法，例如~\cite{lin2021efficient}提出了一种基于局部敏感哈希的自注意力机制，通过减少查询和键之间的点积计算量，从而提高了Transformer模型的计算效率。同样, 这种改进方法仍然无法完全解决Transformer模型的计算效率问题, 因此揭示自注意力机制和状态空间之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
+
+Through the self-attention mechanism, the Transformer model can directly capture the relationship between any two elements in the sequence, effectively handling long-distance dependency problems.
+However, the quadratic complexity of the self-attention mechanism limits the computational efficiency of the Transformer model, making it perform poorly when handling long sequence data.
+To overcome this limitation, researchers have proposed many improvement methods.
+For example, Lin et al.~\cite{lin2021efficient} proposed a self-attention mechanism based on local sensitive hashing, which reduces the computational cost of dot products between queries and keys, thereby improving the computational efficiency of the Transformer model.
+Similarly, this improvement method still cannot completely solve the computational efficiency problem of the Transformer model.
+Therefore, it is very important to reveal the deeper relationship between the self-attention mechanism and the state space and propose a new hybrid modeling architecture to overcome these limitations.
+
 \subsection{Hybrid Modeling}
+% 混合建模架构模型是一种将状态空间和自注意力进行混合建模的模型，其目的是使模型具备与Mamba类似的效率和与Transformer类似的效果。例如，Wonderful Matrices~\cite{shi2024wonderfulmatrices}模型通过将状态空间和自注意力进行混合建模，使得模型能够同时利用状态空间的高效上下文摘要和自注意力有效联想召回的优势。然而，这些模型在情景学习任务上的表现仍然不如原始的Transformer模型，这表明了混合建模架构模型在情景学习任务上的局限性。
+
+Hybrid modeling architecture models are models that combine state-space and self-attention for hybrid modeling, with the goal of making the model have efficiency similar to Mamba and effect similar to Transformer.
+For example, the Wonderful Matrices~\cite{shi2024wonderfulmatrices} model combines state-space and self-attention for hybrid modeling, allowing the model to leverage the advantages of the efficient context summary of the state-space and the effective associative recall of self-attention.
+However, these models still do not perform as well as the original Transformer model in in-context learning tasks, which indicates the limitations of hybrid modeling architecture models in in-context learning tasks.
 

### 2025-01-28 paper.tex
Experiments: two subsection

@@
 \end{aligned}
+\label{eq:state_space}
 \end{equation}
-% \begin{alignat}{2}
-%    h_t &= \overline{A}h_{t-1} + \overline{B}x_t && \tag{2a} \\
-%    y_t &= Ch_t && \tag{2b}
-% % 从连续时间系统的状态空间模型出发，可以通过离散化方法得到离散时间的状态更新公式,方程 (2a) 和 (2b) 代表状态空间模型的离散化形式。它们描述了在离散时间间隔内，状态向量和输出向量如何基于前一个状态和当前输入进行更新。
+% 从连续时间系统的状态空间模型出发，可以通过离散化方法得到离散时间的状态更新公式,方程 (2a) 和 (2b) 代表状态空间模型的离散化形式。它们描述了在离散时间间隔内，状态向量和输出向量如何基于前一个状态和当前输入进行更新。
 % \end{alignat}
@@
 
-         % \end{minipage}
-%          \begin{minipage}{0.45\textwidth}
-%          \begin{alignat}{2}
-%             \overline{K} &= (C\overline{B}, CAB, \ldots, C\overline{A}^k\overline{B}, \ldots) && \tag{3a} \\
-%             y &= x * \overline{K} && \tag{3b}
-%          \end{alignat}
-%          \end{minipage}
-%          % 以上为
-
-%以上为SSM-S4的过程，所有结构化 SSM 都是 LTI 模型，LTI 模型存在基本的效率限制,为了克服这些局限性，研究者们提出了多种改进方法。例如，~\cite{mamba2}模型通过引入选择性扫描算法（Selective Scan）和硬件感知算法（Hardware-Aware Algorithm），使得SSM能够动态调整参数，从而更好地处理长序列数据并提高计算效率。这种改进的SSM，也被称为选择性状态空间模型（Selective SSM，简称S6），追求能够像Transformer一样构建高效的序列处理模块。但是即便如此，它仍然不如CNN 和 Transformer在计算上高效，而现代并行计算设备的发展使得这种计算效率的差距变得更加明显, 从而限制了SSM在更大规模的序列数据上的训练,因此揭示选择性SSM和注意力机制之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
-
+% 以上为SSM-S4的过程，所有结构化 SSM 都是 LTI 模型，LTI 模型存在基本的效率限制,为了克服这些局限性，研究者们提出了多种改进方法。例如，~\cite{mamba2}模型通过引入选择性扫描算法（Selective Scan）和硬件感知算法（Hardware-Aware Algorithm），使得SSM能够动态调整参数，从而更好地处理长序列数据并提高计算效率。这种改进的SSM，也被称为选择性状态空间模型（Selective SSM，简称S6），追求能够像Transformer一样构建高效的序列处理模块。但是即便如此，它仍然不如CNN 和 Transformer在计算上高效，而现代并行计算设备的发展使得这种计算效率的差距变得更加明显, 从而限制了SSM在更大规模的序列数据上的训练,因此揭示选择性SSM和注意力机制之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
 The above is the process of SSM-S4.
@@
    \begin{aligned}
-      Y &= \operatorname*{softmax}({QK^\top}) \cdot V   \end{aligned}
+      Y &= \operatorname*{softmax}({QK^\top}) \cdot V   
+   \end{aligned}
+\label{eq:self_attention}
 \end{equation}
 
-% 通过自注意力机制，Transformer模型能够直接捕捉序列中任意两个元素之间的关系，从而有效处理长距离依赖问题。然而，自注意力机制的二次复杂度限制了Transformer模型的计算效率，使得其在处理长序列数据时表现不佳。为了克服这一局限性，研究者们提出了许多改进方法，例如~\cite{lin2021efficient}提出了一种基于局部敏感哈希的自注意力机制，通过减少查询和键之间的点积计算量，从而提高了Transformer模型的计算效率。同样, 这种改进方法仍然无法完全解决Transformer模型的计算效率问题, 因此揭示自注意力机制和状态空间之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
+% 通过自注意力机制，Transformer模型能够直接捕捉序列中任意两个元素之间的关系，从而有效处理长距离依赖问题。然而，自注意力机制的二次复杂度限制了Transformer模型的计算效率，使得其在处理长序列数据时表现不佳。为了克服这一局限性，研究者们提出了许多改进方法，例如~\cite{kitaev2020reformer}提出了一种基于局部敏感哈希的自注意力机制，通过减少查询和键之间的点积计算量，从而提高了Transformer模型的计算效率。同样, 这种改进方法仍然无法完全解决Transformer模型的计算效率问题, 因此揭示自注意力机制和状态空间之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
 
@@
 To overcome this limitation, researchers have proposed many improvement methods.
-For example, Lin et al.~\cite{lin2021efficient} proposed a self-attention mechanism based on local sensitive hashing, which reduces the computational cost of dot products between queries and keys, thereby improving the computational efficiency of the Transformer model.
+For example, Lin et al.~\cite{kitaev2020reformer} proposed a self-attention mechanism based on local sensitive hashing, which reduces the computational cost of dot products between queries and keys, thereby improving the computational efficiency of the Transformer model.
 Similarly, this improvement method still cannot completely solve the computational efficiency problem of the Transformer model.
@@
 For good extrapolation performance, we can add it to the state space.
-Let's review the state-space algorithm~\ref{}, first, the matrix $B$ controls whether to let the input $x_t$ enter the state $h_t$, we add rotational positional encoding to the matrix $B$, the matrix $B$ as an input gate filters $x_t$ after $h_t$ has absolute positional information, then, the matrix $A$ controls whether to let the state $h_{t-1}$ enter the state $h_t$, that is, it also allows the absolute positional information of the past state to affect the current state, finally, the matrix $C$ controls whether to let the state $h_t$ enter the output $y_t$, we add rotational positional encoding to the matrix $C$, the matrix $C$ as an output gate filters $h_t$ after $y_t$ has relative positional information.
+Let's review the state-space algorithm~\ref{eq:state_space}, first, the matrix $B$ controls whether to let the input $x_t$ enter the state $h_t$, we add rotational positional encoding to the matrix $B$, the matrix $B$ as an input gate filters $x_t$ after $h_t$ has absolute positional information, then, the matrix $A$ controls whether to let the state $h_{t-1}$ enter the state $h_t$, that is, it also allows the absolute positional information of the past state to affect the current state, finally, the matrix $C$ controls whether to let the state $h_t$ enter the output $y_t$, we add rotational positional encoding to the matrix $C$, the matrix $C$ as an output gate filters $h_t$ after $y_t$ has relative positional information.
 However, it is worth noting that due to the recursive nature of the state space, that is, only one state cache is retained, the positional encoding will be affected by the superposition state, even the original one-dimensional convolution positional encoding is the same, which is also its difficulty in context learning defect.
@@
 To solve this problem, we should use self-attention and feed-forward networks that do not compress context information before the LM-Head, which can produce context-aware states by weighting elements without distance restrictions, allowing the model to continue to leverage the efficient context summary of the state space and the effective associative recall of self-attention without bias in the final token prediction.
+
+\section{Experiments}
+
+% 我们使用基线模型Jamba~\cite{lieber2024jamba}架构, 首先构造了一个280M的小型语言模型在语义相似度, 长短文本分类, 自然语言推理, 关键词识别, 多领域多选任务上验证了我们的方法. 然后, 我们将模型规模扩展至1B, 在标准短文本, 自然长文本, 合成长文本, 大海捞针任务上进行了验证. 
+We used the baseline model Jamba~\cite{lieber2024jamba} architecture to first construct a 280M small language model and verified our method on semantic similarity, short text classification, natural language reasoning, keyword recognition, and multi-domain multiple-choice tasks.
+Then, we scaled the model to 1B and verified it on standard short text, natural long text, synthetic long text, and needle in a haystack tasks.
+
+\subsection{Datasets and Hyperparameters}
+% 预训练数据集为包含 Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl 等开源数据集混合而成的数据集.
+The pre-training dataset is a mixed dataset containing open-source datasets such as Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl, etc.
+
+% 学习率调度器公式来源于 Attention is All You Need~\citep{wolf-etal-2020-transformers}.
+The learning rate scheduler function comes from Attention is All You Need~\cite{wolf-etal-2020-transformers}.
+
+\begin{equation}
+\begin{aligned}
+   lr &= d_{model}^{-0.5} \times \min(steps^{-0.5}, steps \times warmup^{-1.5})
+\end{aligned}
+\end{equation}
+
+% 此外, 我们没有使用线性偏置项, 预热步数为总步数的 $10\%$, 使用 $RMSNorm$ 代替 $LayerNorm$, $AdamW$ 超参数设置为 $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, 使用 GLM~\citep{du2022glm} 作为体系结构骨干, 即双向 GLM 通用语言模型: 对训练文本序列跨度 MASK, 以自回归填空作为训练目标, 要求模型预测被 MASK 的 token.
+环境为 NVIDIA 提供的开源 PyTorch 镜像~\citep{pytorch}.
+In addition, we did not use linear bias terms, the warm-up steps were 10\% of the total steps, $RMSNorm$ was used instead of $LayerNorm$, $AdamW$ hyperparameters were set to $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and GLM~\cite{du2022glm} was used as the architecture backbone, that is, bidirectional GLM universal language model: MASK across training text sequence spans, with autoregressive filling as the training target, requiring the model to predict the MASKed token.
+The environment was provided by NVIDIA's open-source PyTorch image~\cite{pytorch}.
+
+\subsection{Self-Attention before LM-Head is Important}
+\label{sec:Self-Attention_before_LM-Head_is_Important}
+
+% 我们在表~\ref{tab:Jamba_vs_Jamba-SABLH_Params} 中展示了 Jamba 和 Jamba-SABLH 的参数设置, 在一个Jamba混合循环中, 我们将最后一个模块从state-space模块修改为self-attention模块, 其余参数设置相同.
+As shown in Table~\ref{tab:Jamba_vs_Jamba-SABLH_Params}, we show the parameter settings of Jamba and Jamba-SABLH.
+In a Jamba hybrid cycle, we modified the last module from a state-space module to a self-attention module, and the rest of the parameters were the same.
+
+% 如表~\ref{tab:Jamba_vs_Jamba-SABLH_Results} 所示, Jamba 与 Jamba-SABLH 在预训练阶段的困惑表现差异微乎其微, 这表明两者从预训练学习到了几乎相同的知识.
+然而, 在 SFT 微调阶段, 模型通常需要根据上文记住特定的格式, 并在下文中基于这些格式进行推理.
+这已经被证实是以递归方式聚合状态信息的 SSM 的能力缺陷.
+而单个 Jamba 块中的 self-attention 部分被嵌入到 state-space 层之间, 导致自注意力的将每个答案的知识直接路由到单个答案 token 的能力所产生的信息状态, 被随后的三个 SSM 层衰减, 最终造成了知识路由的偏差.
+% Jamba-SABLH 在最后一层的将 state-space 所递归聚合的状态信息重新进行了自注意力加权, 这相当于学习并加权了从第一个 token 到最后一个 token 的信息是如何递归聚合的过程. 然后将两种状态信息混合在一起, 这样就有效避免了知识路由偏差. 因此, 我们现在就能够解释为什么 Jamba-SABLH 在大多数验证任务上都有明显优势了.
+As shown in Table~\ref{tab:Jamba_vs_Jamba-SABLH_Results}, the difference in perplexity performance between Jamba and Jamba-SABLH in the pre-training phase is negligible, indicating that the two learned almost the same knowledge from pre-training.
+However, in the SFT fine-tuning phase, the model usually needs to remember specific formats based on the context and reason based on these formats in the subsequent context.
+This has been proven to be a deficiency in the ability of SSM to aggregate state information recursively.
+The self-attention part in a single Jamba block is embedded between the state-space layers, resulting in the information state produced by the ability of self-attention to route the knowledge of each answer directly to a single answer token being decayed by the subsequent three SSM layers, ultimately causing bias in knowledge routing.
+Jamba-SABLH re-weights the state information recursively aggregated by state-space in the last layer with self-attention, which is equivalent to learning and weighting the process of how the information from the first token to the last token is recursively aggregated.
+Then the two state information is mixed together, effectively avoiding bias in knowledge routing.
+Therefore, we can now explain why Jamba-SABLH has a significant advantage in most validation tasks.
+
+% 对于 AFQMC 这类判断句子含义是否相同的任务, CSL这类判断关键词是否在摘要中而非从摘要提取关键词的任务, 以及 CMNLI 这类判断两个句子之间是蕴涵, 中立还是矛盾关系的任务, 它们主要依赖于在序列上选择性地提取关键信息并递归地聚合状态信息.
+因此, Jamba 和 Jamba-SABLH 在这些任务上的表现差距并不显著, 而 Jamba-SABLH 在 AFQMC 和 CSL 上略微领先的原因可能是因为它修正了一些知识路由偏差.
+在 TNEWS 这类对短句进行类别预测的任务中, 由于句子不包含或很少包含上下文信息, 因此非常依赖于预训练和微调的质量.这要求模型在预训练阶段学到的知识能够在微调阶段被正确且精确地引导, 这导致了 Jamba 在 TNEWS 上的表现远不如 Jamba-SABLH.
+与 TNEWS 相反, IFLYTEK 任务中的文本全部为长上下文, 并且其中多次出现所属应用主题的词汇.
+这构成了一个相对简单的单查询关联召回任务, 其中多次出现的单个主题词汇被选择性状态空间模型允许存储在状态中, 并成为主要影响输出的因素.
+因此, 两者在 IFLYTEK 上的表现差距不大.
+在 WSC 这类代词消歧任务中, 模型需要在代词出现后能够逆向追溯到代词之前出现的名词, 并将代词指向正确的名词.
+这属于在单查询联想回忆任务中, 额外要求了对当前语言的理解能力.
+因此, 两者在 WSC 上的表现差距在这些任务中排名第二的原因就很明显了, 两个主要因素是微调的质量差距以及 Jamba-SABLH 预测前对长期强依赖关系逐渐衰减的递归聚合信息的重新全元素关注.
+For tasks like AFQMC that judge whether sentences have the same meaning, CSL that judge whether keywords are in the abstract rather than extracting keywords from the abstract, and CMNLI that judge whether two sentences imply, are neutral, or are contradictory, they mainly rely on selectively extracting key information on the sequence and recursively aggregating state information.
+Therefore, the performance gap between Jamba and Jamba-SABLH on these tasks is not significant, and the slight lead of Jamba-SABLH on AFQMC and CSL may be due to it correcting some knowledge routing bias.
+In tasks like TNEWS that predict the category of short sentences, since the sentences do not contain or contain very little context information, they rely heavily on the quality of pre-training and fine-tuning.
+This requires that the knowledge learned by the model in the pre-training phase can be correctly and accurately guided in the fine-tuning phase, resulting in Jamba's performance on TNEWS being far worse than Jamba-SABLH.
+In contrast to TNEWS, the text in the IFLYTEK task is all long context, and the vocabulary of the application topic appears multiple times.
+This constitutes a relatively simple single-query associative recall task, where the selectively stored single topic vocabulary that appears multiple times is allowed to be stored in the state by the selective state-space model and becomes the main factor affecting the output.
+Therefore, the performance gap between the two on IFLYTEK is not significant.
+In tasks like WSC that require pronoun disambiguation, the model needs to be able to trace back to the noun that appeared before the pronoun after the pronoun appears and point the pronoun to the correct noun.
+This belongs to the additional requirement of understanding the current language in the single-query associative recall task.
+Therefore, the reason for the performance gap between the two on WSC is obvious in these tasks, the two main factors are the difference in the quality of fine-tuning and the re-attention of the recursively aggregated information that gradually decays the long-term strong dependency relationship before prediction by Jamba-SABLH.
+
+\begin{table*}[!htbp]
+   \centering
+   \caption{
+      \textbf{Parameters of Jamba and Jamba-SABLH}.
+      % 在原始Jamba论文中, 每8层为一个混合循环, 包括7个state-space模块, 1个self-attention模块, 和8个MLP模块.
+我们仅将最后一个模块修改为self-attention模块, 其余参数设置与Jamba相同, 构造了两个280M左右的模型, 分别是Jamba和Jamba-SABLH.
+混合结构中使用S代表state-space模块, A代表self-attention模块, M代表MLP模块.
+      In the original Jamba paper, every 8 layers are a hybrid cycle, including 7 state-space modules, 1 self-attention module, and 8 MLP modules.
+We only modified the last module to a self-attention module, and the rest of the parameters are the same as Jamba.
+We constructed two models of about 280M, Jamba and Jamba-SABLH.
+In the hybrid structure, S represents the state-space module, A represents the self-attention module, and M represents the MLP module.
+   }
+   \label{tab:Jamba_vs_Jamba-SABLH_Params}
+   \begin{tabular}{@{}lllllllll@{}}
+   \toprule
+   \sc{Model} & \sc{Params} & $n_{layers}$ & $d_{model}$ & $d_{ffn}$ & $n_{heads}$ & $d_{state}$ & \sc{Hybrid} \\
+   \midrule
+   Jamba & 283M & 8 & 1024 & 4096 & 16 & 16 & SMSMSMSMAMSMSMSM \\
+   Jamba-SABLH & 281M & 8 & 1024 & 4096 & 16 & 16 & SMSMSMSMAMSMSMAM \\
+   \bottomrule
+   \end{tabular}
+\end{table*}
+
+\begin{table*}[!htbp]
+   \centering
+   \caption{
+      \textbf{Results of Jamba and Jamba-SABLH}.
+      %  Jamba 与 Jamba-SABLH 在预训练上的困惑表现差距并不大, 但是在进行 SFT 微调时, Jamba-SABLH 的困惑值明显低于 Jamba. 我们选取了 CLUEbenchmark~\cite{xu-etal-2020-clue} 中对于当前参数量较为合适的评估任务: 
+      % AFQMC: 语义相似度, 判断两个句子是含义相同还是不同.
+      % TNEWS: 短文本分类, 来自今日头条的新闻板块, 判断新闻的所属类别.
+      % IFLYTEK: 长文本分类, 关于软件描述的长文本数据集, 判断软件描述的所属应用主题.
+      % CMNLI: 语言推理, 判断两个句子之间的逻辑关系.
+      % WSC: 代词消歧, 判断句子中的代词指代的是哪个名词.
+      % CSL: 关键词识别, 取自论文摘要及其关键词, 判断关键词是否在摘要中.
+      % 在AFQMC, TNEWS, IFLYTEK, WSC, CSL 的验证集推断准确率上 Jamba-SABLH 均保持领先, 在 CMNLI 上略有落后, 平均准确率上 Jamba-SABLH 较 Jamba 提升了 $4.25\%$.
+      The performance gap between Jamba and Jamba-SABLH in pre-training perplexity is not large, but in SFT fine-tuning, the perplexity of Jamba-SABLH is significantly lower than Jamba.
+We selected the evaluation tasks in CLUEbenchmark~\cite{xu-etal-2020-clue} that are more suitable for the current parameter volume:
+      AFQMC: Semantic similarity, judge whether two sentences have the same meaning or not.
+      TNEWS: Short text classification, from the news section of today's headlines, judge the category of news.
+      IFLYTEK: Long text classification, a long text dataset about software descriptions, judge the application topic of the software description.
+      CMNLI: Language reasoning, judge the logical relationship between two sentences.
+      WSC: Pronoun disambiguation, judge which noun the pronoun in the sentence refers to.
+      CSL: Keyword recognition, taken from the abstract and keywords of the paper, judge whether the keyword is in the abstract.
+      In the validation set inference accuracy of AFQMC, TNEWS, IFLYTEK, WSC, CSL, Jamba-SABLH maintains the lead, slightly behind in CMNLI, and the average accuracy of Jamba-SABLH is $4.25\%$ higher than Jamba.
+   }
+   \label{tab:Jamba_vs_Jamba-SABLH_Results}
+   \begin{tabular}{@{}llllllllll@{}}
+   \toprule
+   \sc{Model} & \sc{PT} & \sc{SFT} & \sc{AFQMC} & \sc{TNEWS} & \sc{IFLYTEK} & \sc{CMNLI} & \sc{WSC} & \sc{CSL} & \sc{Average} \\
+   & \sc{ppl $\downarrow$} & \sc{ppl $\downarrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} \\
+   \midrule
+   Jamba & 2.53 & 1.98 & 78.65 & 63.15 & 72.40 & 79.66 & 76.64 & 84.83 & 75.89 \\
+   Jamba-SABLH & 2.51 & 1.69 & 79.48 & 77.98 & 72.71 & 79.59 & 79.93 & 85.06 & 79.12 \\
+   \bottomrule
+   \end{tabular}
+\end{table*}
+
+\subsection{Associative Recall}
+\label{sec:Associative_Recall}
+
+% 我们在序列长度为 2048 的 80\% 的预训练数据集上训练了 1B 参数的 Jamba 模型与 1B 参数的 OTCE 模型,  然后将剩余的 20\% 的预训练数据集打包为 8K 上下文长度的数据集继续对模型进行预训练, 随后将微调数据集同样打包为 8K 上下文长度的数据集对模型进行微调, 将两个模型扩展到 8K 长度的上下文长度进行评估, 两个模型的参数设置如表~\ref{tab:associative_recall_params_zh} 所示.
 

### 2025-01-28 paper.tex
Experiments: two subsection

@@
 % 预训练数据集为包含 Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl 等开源数据集混合而成的数据集.
-The pre-training dataset is a mixed dataset containing open-source datasets such as Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl, etc.
+The pre-training dataset is a mixed dataset containing open-source datasets such as Book~\cite{bookcrossing_dataset}, Wikipedia~\cite{wikipedia_dataset}, UNCorpus~\cite{uncorpus_dataset}, translation2019zh~\cite{translation2019zh_dataset}, WikiMatri~\cite{WikiMatri}, news-commentry~\cite{newscommentary_dataset}, ParaCrawlv9~\cite{paracrawl_dataset}, ClueCorpusSmall~\cite{cluecorpusSmall_dataset}, CSL~\cite{li-etal-2022-csl}, news-crawl~\cite{newscrawl_dataset}, etc.
 
@@
 
-\subsection{Associative Recall}
-\label{sec:Associative_Recall}
-
-% 我们在序列长度为 2048 的 80\% 的预训练数据集上训练了 1B 参数的 Jamba 模型与 1B 参数的 OTCE 模型,  然后将剩余的 20\% 的预训练数据集打包为 8K 上下文长度的数据集继续对模型进行预训练, 随后将微调数据集同样打包为 8K 上下文长度的数据集对模型进行微调, 将两个模型扩展到 8K 长度的上下文长度进行评估, 两个模型的参数设置如表~\ref{tab:associative_recall_params_zh} 所示.
-
 \bibliography{paper}

### 2025-01-29 paper.tex
Update Experiments: done

--- 2025-01-28 paper.tex
@@
 % 但是, 目前主流的混合建模架构模型在情景学习任务上的表现并不理想, 我们重新审视了这两种算法的优势和劣势, 从原理出发对这种混合建模的结构重新设计. 
-% 最终, 重新设计的架构, 在标准短文本任务中提升了 1.3 \% 效果, 在自然长文本任务中提升了 20.86 \% 效果, 在合成长文本任务中提升了 27.06 \% 效果.
+% 最终, 重新设计的架构, 在标准短文本任务中提升了 1.1 \% 效果, 在自然长文本任务中提升了 20.86 \% 效果, 在合成长文本任务中提升了 24.15 \% 效果.
 Recent research has shown that combining the state-space algorithm-driven Mamba with the self-attention algorithm-driven Transformer outperforms using Mamba or Transformer alone in most language modeling tasks.
@@
 We re-examine the advantages and disadvantages of these two algorithms and redesign the structure of this hybrid modeling from the principle.
-The finally redesigned architecture improves the performance by 1.3\% in standard short text tasks, 20.86\% in natural long text tasks, and 27.06\% in synthetic long text tasks.
+The finally redesigned architecture improves the performance by 1.1\% in standard short text tasks, 20.86\% in natural long text tasks, and 24.15\% in synthetic long text tasks.
 \end{abstract}
@@
 % 我们的研究与评估表明, Self-Attention before LM-Head 只需要很少的结构与参数调整, 就能够与基线混合模型相比, 在上下文学习任务基准上取得更好的性能.
-例如, 在标准短文本任务中, 我们的模型提升了 1.3 \% 的效果, 在自然长文本任务中提升了 20.86 \% 的效果, 在合成长文本任务中提升了 27.06 \% 的效果, 并且在大海捞针任务上取得了最先进的效果.
+例如, 在标准短文本任务中, 我们的模型提升了 1.1 \% 的效果, 在自然长文本任务中提升了 20.86 \% 的效果, 在合成长文本任务中提升了 24.15 \% 的效果, 并且在大海捞针任务上取得了最先进的效果.
 Our research and evaluation show that Self-Attention before LM-Head can achieve better performance on the in-context learning task benchmark compared to the baseline hybrid model with only a few structural and parameter adjustments.
-For example, in standard short text tasks, our model improves performance by 1.3\%, in natural long text tasks by 20.86\%, in synthetic long text tasks by 27.06\%, and achieves state-of-the-art performance on the needle in a haystack task.
+For example, in standard short text tasks, our model improves performance by 1.1\%, in natural long text tasks by 20.86\%, in synthetic long text tasks by 24.15\%, and achieves state-of-the-art performance on the needle in a haystack task.
 
@@
       }
-      \textbf{}
-
    \label{fig:architecture}
@@
 % 预训练数据集为包含 Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl 等开源数据集混合而成的数据集.
-The pre-training dataset is a mixed dataset containing open-source datasets such as Book, Wikipedia, UNCorpus, translation2019zh, WikiMatri, news-commentry, ParaCrawlv9, ClueCorpusSmall, CSL, news-crawl, etc.
+The pre-training dataset is a mixed dataset containing open-source datasets such as Book~\cite{bookcrossing_dataset}, Wikipedia~\cite{wikipedia_dataset}, UNCorpus~\cite{uncorpus_dataset}, translation2019zh~\cite{translation2019zh_dataset}, WikiMatri~\cite{wikimatri_dataset}, news-commentry~\cite{newscommentary_dataset}, ParaCrawlv9~\cite{paracrawl_dataset}, ClueCorpusSmall~\cite{cluecorpusSmall_dataset}, CSL~\cite{li-etal-2022-csl}, news-crawl~\cite{newscrawl_dataset}, etc.
 
@@
 In a Jamba hybrid cycle, we modified the last module from a state-space module to a self-attention module, and the rest of the parameters were the same.
+
+\begin{table*}[!htbp]
+   \centering
+   \caption{
+      \textbf{Parameters of Jamba and Jamba-SABLH for Verification}.
+      % 在原始Jamba论文中, 每8层为一个混合循环, 包括7个state-space模块, 1个self-attention模块, 和8个MLP模块.
+我们仅将最后一个模块修改为self-attention模块, 其余参数设置与Jamba相同, 构造了两个280M左右的模型, 分别是Jamba和Jamba-SABLH.
+混合结构中使用S代表state-space模块, A代表self-attention模块, M代表MLP模块.
+      In the original Jamba paper, every 8 layers are a hybrid cycle, including 7 state-space modules, 1 self-attention module, and 8 MLP modules.
+We only modified the last module to a self-attention module, and the rest of the parameters are the same as Jamba.
+We constructed two models of about 280M, Jamba and Jamba-SABLH.
+In the hybrid structure, S represents the state-space module, A represents the self-attention module, and M represents the MLP module.
+   }
+   \label{tab:Jamba_vs_Jamba-SABLH_Params}
+   \vskip 0.15in
+   \begin{tabular}{@{}lllllllll@{}}
+   \toprule
+   \sc{Model} & \sc{Params} & $n_{layers}$ & $d_{model}$ & $d_{ffn}$ & $n_{heads}$ & $d_{state}$ & \sc{Hybrid} \\
+   \midrule
+   Jamba & 283M & 8 & 1024 & 4096 & 16 & 16 & SMSMSMSMAMSMSMSM \\
+   Jamba-SABLH & 281M & 8 & 1024 & 4096 & 16 & 16 & SMSMSMSMAMSMSMAM \\
+   \bottomrule
+   \end{tabular}
+\end{table*}
+
+\begin{table*}[!htbp]
+   \centering
+   \caption{
+      \textbf{Results of Jamba and Jamba-SABLH for Verification}.
+      %  Jamba 与 Jamba-SABLH 在预训练上的困惑表现差距并不大, 但是在进行 SFT 微调时, Jamba-SABLH 的困惑值明显低于 Jamba. 我们选取了 CLUEbenchmark~\cite{xu-etal-2020-clue} 中对于当前参数量较为合适的评估任务: 
+      % AFQMC: 语义相似度, 判断两个句子是含义相同还是不同.
+      % TNEWS: 短文本分类, 来自今日头条的新闻板块, 判断新闻的所属类别.
+      % IFLYTEK: 长文本分类, 关于软件描述的长文本数据集, 判断软件描述的所属应用主题.
+      % CMNLI: 语言推理, 判断两个句子之间的逻辑关系.
+      % WSC: 代词消歧, 判断句子中的代词指代的是哪个名词.
+      % CSL: 关键词识别, 取自论文摘要及其关键词, 判断关键词是否在摘要中.
+      % 在AFQMC, TNEWS, IFLYTEK, WSC, CSL 的验证集推断准确率上 Jamba-SABLH 均保持领先, 在 CMNLI 上略有落后, 平均准确率上 Jamba-SABLH 较 Jamba 提升了 $4.25\%$.
+      The performance gap between Jamba and Jamba-SABLH in pre-training perplexity is not large, but in SFT fine-tuning, the perplexity of Jamba-SABLH is significantly lower than Jamba.
+We selected the evaluation tasks in CLUEbenchmark~\cite{xu-etal-2020-clue} that are more suitable for the current parameter volume:
+      AFQMC: Semantic similarity, judge whether two sentences have the same meaning or not.
+      TNEWS: Short text classification, from the news section of today's headlines, judge the category of news.
+      IFLYTEK: Long text classification, a long text dataset about software descriptions, judge the application topic of the software description.
+      CMNLI: Language reasoning, judge the logical relationship between two sentences.
+      WSC: Pronoun disambiguation, judge which noun the pronoun in the sentence refers to.
+      CSL: Keyword recognition, taken from the abstract and keywords of the paper, judge whether the keyword is in the abstract.
+      In the validation set inference accuracy of AFQMC, TNEWS, IFLYTEK, WSC, CSL, Jamba-SABLH maintains the lead, slightly behind in CMNLI, and the average accuracy of Jamba-SABLH is $4.25\%$ higher than Jamba.
+   }
+   \label{tab:Jamba_vs_Jamba-SABLH_Results}
+   \vskip 0.15in
+   \begin{tabular}{@{}llllllllll@{}}
+   \toprule
+   \sc{Model} & \sc{PT} & \sc{SFT} & \sc{AFQMC} & \sc{TNEWS} & \sc{IFLYTEK} & \sc{CMNLI} & \sc{WSC} & \sc{CSL} & \sc{Average} \\
+   & \sc{ppl $\downarrow$} & \sc{ppl $\downarrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} \\
+   \midrule
+   Jamba & 12.55 & 7.24 & 78.65 & 63.15 & 72.40 & 79.66 & 76.64 & 84.83 & 75.89 \\
+   Jamba-SABLH & 12.30 & 5.42 & 79.48 & 77.98 & 72.71 & 79.59 & 79.93 & 85.06 & 79.12 \\
+   \bottomrule
+   \end{tabular}
+\end{table*}
 
@@
 \begin{table*}[!htbp]
+   \footnotesize
    \centering
    \caption{
-      \textbf{Parameters of Jamba and Jamba-SABLH}.
-      % 在原始Jamba论文中, 每8层为一个混合循环, 包括7个state-space模块, 1个self-attention模块, 和8个MLP模块.
-我们仅将最后一个模块修改为self-attention模块, 其余参数设置与Jamba相同, 构造了两个280M左右的模型, 分别是Jamba和Jamba-SABLH.
-混合结构中使用S代表state-space模块, A代表self-attention模块, M代表MLP模块.
-      In the original Jamba paper, every 8 layers are a hybrid cycle, including 7 state-space modules, 1 self-attention module, and 8 MLP modules.
-We only modified the last module to a self-attention module, and the rest of the parameters are the same as Jamba.
-We constructed two models of about 280M, Jamba and Jamba-SABLH.
-In the hybrid structure, S represents the state-space module, A represents the self-attention module, and M represents the MLP module.
+      \textbf{Parameters of Jamba and Jamba-SABLH for Associative Recall}.
+      % Jamba的混合循环相当于循环表~\ref{tab:Jamba_vs_Jamba-SABLH_Params} 中的混合配置三次, Jamba-SABLH 除了最后一层的 self-attention 模块外, 其余参数设置与 Jamba 相同. 除此之外, 我们还是用混合专家作为前馈网络来减少训练成本. 我们通过仔细地调整 $d_ffn$ 来使参数量保持在 1B.
+      The hybrid cycle of Jamba is equivalent to the hybrid configuration in Table~\ref{tab:Jamba_vs_Jamba-SABLH_Params} three times, and Jamba-SABLH is the same as Jamba except for the last layer of the self-attention module.
+In addition, we use mixture of experts as the feed-forward network to reduce training costs.
+We carefully adjusted $d_{ffn}$ to keep the parameter volume at 1B.
    }
-   \label{tab:Jamba_vs_Jamba-SABLH_Params}
-   \begin{tabular}{@{}lllllllll@{}}
+   \label{tab:associative_recall_params}
+   \vskip 0.15in
+   \begin{tabular}{@{}llllllllllllllllll@{}}
    \toprule
-   \sc{Model} & \sc{Params} & $n_{layers}$ & $d_{model}$ & $d_{ffn}$ & $n_{heads}$ & $d_{state}$ & \sc{Hybrid} \\
+   \sc{Model} & \sc{Params} & $n_{layers}$ & $d_{model}$ & $n_{heads}$ & $d_{state}$ & $n_{experts}$ & $top_{experts}$ \\
    \midrule
-   Jamba & 283M & 8 & 1024 & 4096 & 16 & 16 & SMSMSMSMAMSMSMSM \\
-   Jamba-SABLH & 281M & 8 & 1024 & 4096 & 16 & 16 & SMSMSMSMAMSMSMAM \\
+   Jamba & 1B & 24 & 1024 & 16 & 64 & 4 & 1 \\
+   Jamba-SABLH & 1B & 24 & 1024 & 16 & 64 & 4 & 1 \\
    \bottomrule
@@
    \caption{
-      \textbf{Results of Jamba and Jamba-SABLH}.
-      %  Jamba 与 Jamba-SABLH 在预训练上的困惑表现差距并不大, 但是在进行 SFT 微调时, Jamba-SABLH 的困惑值明显低于 Jamba. 我们选取了 CLUEbenchmark~\cite{xu-etal-2020-clue} 中对于当前参数量较为合适的评估任务: 
-      % AFQMC: 语义相似度, 判断两个句子是含义相同还是不同.
-      % TNEWS: 短文本分类, 来自今日头条的新闻板块, 判断新闻的所属类别.
-      % IFLYTEK: 长文本分类, 关于软件描述的长文本数据集, 判断软件描述的所属应用主题.
-      % CMNLI: 语言推理, 判断两个句子之间的逻辑关系.
-      % WSC: 代词消歧, 判断句子中的代词指代的是哪个名词.
-      % CSL: 关键词识别, 取自论文摘要及其关键词, 判断关键词是否在摘要中.
-      % 在AFQMC, TNEWS, IFLYTEK, WSC, CSL 的验证集推断准确率上 Jamba-SABLH 均保持领先, 在 CMNLI 上略有落后, 平均准确率上 Jamba-SABLH 较 Jamba 提升了 $4.25\%$.
-      The performance gap between Jamba and Jamba-SABLH in pre-training perplexity is not large, but in SFT fine-tuning, the perplexity of Jamba-SABLH is significantly lower than Jamba.
-We selected the evaluation tasks in CLUEbenchmark~\cite{xu-etal-2020-clue} that are more suitable for the current parameter volume:
-      AFQMC: Semantic similarity, judge whether two sentences have the same meaning or not.
-      TNEWS: Short text classification, from the news section of today's headlines, judge the category of news.
-      IFLYTEK: Long text classification, a long text dataset about software descriptions, judge the application topic of the software description.
-      CMNLI: Language reasoning, judge the logical relationship between two sentences.
-      WSC: Pronoun disambiguation, judge which noun the pronoun in the sentence refers to.
-      CSL: Keyword recognition, taken from the abstract and keywords of the paper, judge whether the keyword is in the abstract.
-      In the validation set inference accuracy of AFQMC, TNEWS, IFLYTEK, WSC, CSL, Jamba-SABLH maintains the lead, slightly behind in CMNLI, and the average accuracy of Jamba-SABLH is $4.25\%$ higher than Jamba.
+      \textbf{Results of Jamba and Jamba-SABLH for Associative Recall}.
+      % 我们对联想回忆的验证任务选取包括: 标准短上下文任务: PIQA~\cite{bisk2020piqa}, 自然长上下文任务: NarrativeQA~\cite{kovcisky2018narrativeqa}, 合成长上下文任务: HotpotQA~\cite{yang2018hotpotqa}.
+我们在这三个任务上评估 Jamba 与 Jamba-SABLH 在这三个任务上的表现.
+Jamba-SABLH 在标准短上下文任务上提升了 $1.1\%$, 在自然长上下文任务上提升了 $20.86\%$, 在合成长上下文任务上提升了 $24.15\%$, 平均提升了 $10.24\%$.
+      We selected associative recall validation tasks including: standard short context task: PIQA~\cite{bisk2020piqa}, natural long context task: NarrativeQA~\cite{kovcisky2018narrativeqa}, synthetic long context task: HotpotQA~\cite{yang2018hotpotqa}.
+We evaluated the performance of Jamba and Jamba-SABLH on these three tasks.
+Jamba-SABLH improved by $1.1\%$ on the standard short context task, $20.86\%$ on the natural long context task, $24.15\%$ on the synthetic long context task, and an average improvement of $10.24\%$.
    }
-   \label{tab:Jamba_vs_Jamba-SABLH_Results}
-   \begin{tabular}{@{}llllllllll@{}}
+   \label{tab:associative_recall_results}
+   \vskip 0.15in
+   \begin{tabular}{@{}lllllll@{}}
    \toprule
-   \sc{Model} & \sc{PT} & \sc{SFT} & \sc{AFQMC} & \sc{TNEWS} & \sc{IFLYTEK} & \sc{CMNLI} & \sc{WSC} & \sc{CSL} & \sc{Average} \\
-   & \sc{ppl $\downarrow$} & \sc{ppl $\downarrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} \\
+   \sc{Model} & \sc{PIQA} & \sc{NarrativeQA} & \sc{HotpotQA} & \sc{Average} \\
+   & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} & \sc{acc $\uparrow$} \\
    \midrule
-   Jamba & 2.53 & 1.98 & 78.65 & 63.15 & 72.40 & 79.66 & 76.64 & 84.83 & 75.89 \\
-   Jamba-SABLH & 2.51 & 1.69 & 79.48 & 77.98 & 72.71 & 79.59 & 79.93 & 85.06 & 79.12 \\
+   Jamba & 78.65 & 23.15 & 34.40 & 45.40 \\
+   Jamba-SABLH & 79.48 & 27.98 & 42.71 & 50.05 \\
    \bottomrule
@@
 \label{sec:Associative_Recall}
+% 我们在序列长度为 2048 的 80\% 的预训练数据集上训练了 1B 参数的 Jamba 与 Jamba-SABLH 模型, 然后将剩余的 20\% 的预训练数据集打包为 8192 上下文长度的数据集继续对模型进行预训练, 随后将微调数据集同样打包为 8192 上下文长度的数据集对模型进行微调, 将两个模型扩展到 8192 长度的上下文长度进行评估, 两个模型的参数设置如表~\ref{tab:associative_recall_params} 所示.
+We trained 1B parameter Jamba and Jamba-SABLH models on 80\% of the pre-training dataset with a sequence length of 2048, then packaged the remaining 20\% of the pre-training dataset into a dataset with a context length of 8192 to continue pre-training the model.
+Then the fine-tuning dataset was also packaged into a dataset with a context length of 8192 to fine-tune the model.
+The two models were extended to a context length of 8192 for evaluation, and the parameter settings of the two models are shown in Table~\ref{tab:associative_recall_params}.
 
-% 我们在序列长度为 2048 的 80\% 的预训练数据集上训练了 1B 参数的 Jamba 模型与 1B 参数的 OTCE 模型,  然后将剩余的 20\% 的预训练数据集打包为 8K 上下文长度的数据集继续对模型进行预训练, 随后将微调数据集同样打包为 8K 上下文长度的数据集对模型进行微调, 将两个模型扩展到 8K 长度的上下文长度进行评估, 两个模型的参数设置如表~\ref{tab:associative_recall_params_zh} 所示.
+% 在表~\ref{tab:associative_recall_results} 中, 我们展示了 Jamba 与 Jamba-SABLH 在联想回忆任务上的表现, 包括标准短上下文任务, 自然长上下文任务, 合成长上下文任务.
+在标准短上下文任务中, 显然不需要模型具备处理长距离依赖的能力.
+我们的目标是评估在常规任务中, 当 Jamba-SABLH 模型被扩展到能够处理长上下文环境时, 其短距离联想召回的精确度是否会受到影响.
+实验结果表明, 在标准短上下文任务上, Jamba-SABLH 的性能优于 Jamba.
+因此 Jamba-SABLH 在适应长上下文环境的同时, 并未牺牲在常见任务上的精度.
+在自然长上下文任务上, Jamba-SABLH 相较于 Jamba 实现了高达 $20.86\%$ 的性能提升.
+我们分析认为, 这种提升的主要原因是 state-space 在训练阶段具有可学习的矩阵 $(A, B, C)$.
+然而在推理阶段, 尽管可以根据不同的输入数据动态计算这些矩阵的值, 但用于这些计算的参数 (即决定如何计算这些矩阵和步长的函数或映射) 是固定的, 这些参数在训练阶段确定后, 在推理阶段被重新使用.
+这导致 state-space 的状态在推理时可能仍然会受到与问题无关的文档的影响.
+相比之下, Jamba 的最后一层由 state-space 和 MLP 组成.
+在推理时, 不仅输出状态在接近输出时可能受到混淆, 输出状态还可能产生不稳定性.
+这些因素共同作用, 导致 Jamba 在处理长上下文任务时的表现不如 Jamba-SABLH.
+% 众所周知, Transformers 模型往往倾向于复制上下文示例中的答案, 而非预测实际问题的答案.
+与此相反, SSMs 模型则更倾向于预测答案, 而难以直接从上文中复制答案.
+在合成长上下文任务中, 模型需要从大量无关的文本中检索信息, 并展现出跨上下文的跟踪和聚合信息的能力.
+Jamba-SABLH 在综合长上下文任务上相比 Jamba 表现出 $24.15\%$ 的优势, 其背后的原因与之前章节~\ref{sec:Self-Attention_before_LM-Head_is_Important} 中讨论的注意力衰减和知识路由偏差问题相似.
+Jamba-SABLH 通过对长期依赖关系逐渐衰减的递归聚合信息进行重新全元素关注加权, 并学习 SSM 如何递归聚合信息的过程来修正知识路由偏差.
+这一机制平衡了复制上下文示例中的答案与预测实际问题的答案的能力, 使得 Jamba-SABLH 能够在处理综合长上下文任务时展现出更优越的性能, 超越了 Jamba.
+As shown in Table~\ref{tab:associative_recall_results}, we show the performance of Jamba and Jamba-SABLH on associative recall tasks, including standard short context tasks, natural long context tasks, and synthetic long context tasks.
+In the standard short context task, it is obvious that the model does not need to have the ability to handle long-distance dependencies.
+Our goal is to evaluate whether the accuracy of short-distance associative recall of Jamba-SABLH will be affected when the Jamba-SABLH model is extended to handle long-context environments in common tasks.
+The experimental results show that Jamba-SABLH outperforms Jamba in the standard short context task.
+Therefore, Jamba-SABLH does not sacrifice accuracy in common tasks while adapting to long-context environments.
+In the natural long context task, Jamba-SABLH achieved a performance improvement of up to $20.86\%$ compared to Jamba.
+We believe that the main reason for this improvement is that the state-space has a learnable matrix $(A, B, C)$ in the training phase.
+However, in the inference phase, although the values of these matrices can be dynamically calculated according to different input data, the parameters used for these calculations (i.e., the function or mapping that determines how to calculate these matrices and the step size) are fixed, and these parameters are reused in the inference phase after being determined in the training phase.
+This means that the state of the state-space may still be influenced by irrelevant documents during inference.
+In contrast, the last layer of Jamba consists of state-space and MLP.
+In inference, not only the output state may be confused when approaching the output, but the output state may also be unstable.
+These factors together result in Jamba's performance in handling long-context tasks being inferior to Jamba-SABLH.
+It is well known that Transformers models tend to copy the answers in the context examples rather than predict the actual answers to the questions.
+In contrast, SSMs models tend to predict answers and are difficult to copy answers directly from the context.
+In the synthetic long context task, the model needs to retrieve information from a large amount of irrelevant text and demonstrate the ability to track and aggregate information across contexts.
+Jamba-SABLH outperforms Jamba by $24.15\%$ in the synthetic long context task, and the reasons behind it are similar to the attention decay and knowledge routing bias discussed in the previous section~\ref{sec:Self-Attention_before_LM-Head_is_Important}.
+Jamba-SABLH corrects the knowledge routing bias by re-attending to the recursively aggregated information that gradually decays the long-term dependency relationship and learns how SSMs recursively aggregate information.
+This mechanism balances the ability to copy answers from context examples and predict actual answers to questions, enabling Jamba-SABLH to demonstrate superior performance in handling synthetic long context tasks, surpassing Jamba.
+
+\begin{figure*}[ht]
+   \centering
+   \includegraphics[width=\linewidth]{fig/needle-in-a-haystack.pdf}
+   \caption{
+     \textbf{Needle in a Haystack}.
+      % 不同架构的模型在 Needle in a Haystack 任务上的表现.
+我们在不同上下文长度对单独使用state-space的Mamba2~\cite{mamba2}, 单独使用self-attention的Llama3~\cite{grattafiori2024llama3herdmodels}, 使用state-space和self-attention混合算法的Jamba, 以及我们的方法Jamba-SABLH进行了评估.
+我们的方法表现出最佳性能.
+      Performance of models with different architectures on the Needle in a Haystack task.
+We evaluated Mamba2~\cite{mamba2} using state-space alone, Llama3~\cite{grattafiori2024llama3herdmodels} using self-attention alone, Jamba using a hybrid algorithm of state-space and self-attention, and our method Jamba-SABLH on different context lengths.
+Our method shows the best performance.
+      }
+   \label{fig:niah}
+\end{figure*}
+
+\subsection{Needle in a Haystack}
+
+% 我们进一步在合成检索任务的大海捞针中比较 Jamba-SABLH, Jamba, Llama3, Mamba2 的性能.
+一个随机且有信息的句子 (即针) 被插入到长文档 (即大海) 中, 并要求模型从大海中检索出针以回答问题.
+所有模型的大小都是 1B, 并且使用相同的设置进行训练: 预训练数据集的 80\% 使用 2048 序列长度, 剩余 20\% 的数据集使用 8192 序列长度进行预训练, 微调数据集同样使用 8192 序列长度进行微调.
+如图~\ref{fig:niah} 所示, Jamba-SABLH 模型显著优于Mamba2, Llama3 和 Jamba.
+We further compare the performance of Jamba-SABLH, Jamba, Llama3, and Mamba2 in the synthetic retrieval task Needle in a Haystack.
+A random and informative sentence (i.e., needle) is inserted into a long document (i.e., haystack), and the model is required to retrieve the needle from the haystack to answer the question.
+All models are of size 1B and trained with the same settings: 80\% of the pre-training dataset uses a sequence length of 2048, the remaining 20\% of the dataset uses a sequence length of 8192 for pre-training, and the fine-tuning dataset also uses a sequence length of 8192 for fine-tuning.
+As shown in Figure~\ref{fig:niah}, the Jamba-SABLH model significantly outperforms Mamba2, Llama3, and Jamba.
 

### 2025-01-30 paper.tex
edit

@@
 \subsection{Hybrid Modeling}
-% 混合建模架构模型是一种将状态空间和自注意力进行混合建模的模型，其目的是使模型具备与Mamba类似的效率和与Transformer类似的效果。例如，Wonderful Matrices~\cite{shi2024wonderfulmatrices}模型通过将状态空间和自注意力进行混合建模，使得模型能够同时利用状态空间的高效上下文摘要和自注意力有效联想召回的优势。然而，这些模型在情景学习任务上的表现仍然不如原始的Transformer模型，这表明了混合建模架构模型在情景学习任务上的局限性。
+% 混合建模架构模型是一种将状态空间和自注意力进行混合建模的模型，其目的是使模型具备与Mamba类似的效率和与Transformer类似的效果。例如，jamba~\cite{lieber2024jamba}模型是一种基于混合建模架构的通用语言模型，其基本结构为8层混合循环，每个混合循环包括7个state-space模块、1个self-attention模块和8个MLP模块。通过将状态空间和自注意力进行混合建模，jamba模型能够在大多数语言建模任务上取得更好的性能。基于混合建模架构的模型在大多数语言建模任务上的表现超越了单独使用Mamba或Transformer，但是在情景学习任务上的表现并不理想。
 
 Hybrid modeling architecture models are models that combine state-space and self-attention for hybrid modeling, with the goal of making the model have efficiency similar to Mamba and effect similar to Transformer.
-For example, the Wonderful Matrices~\cite{shi2024wonderfulmatrices} model combines state-space and self-attention for hybrid modeling, allowing the model to leverage the advantages of the efficient context summary of the state-space and the effective associative recall of self-attention.
-However, these models still do not perform as well as the original Transformer model in in-context learning tasks, which indicates the limitations of hybrid modeling architecture models in in-context learning tasks.
+For example, the Jamba~\cite{lieber2024jamba} model is a universal language model based on a hybrid modeling architecture, with a basic structure of 8 layers of hybrid cycles, each hybrid cycle consisting of 7 state-space modules, 1 self-attention module, and 8 MLP modules.
+By combining state-space and self-attention for hybrid modeling, the Jamba model can achieve better performance on most language modeling tasks.
+Models based on hybrid modeling architecture outperform using Mamba or Transformer alone in most language modeling tasks, but their performance in in-context learning tasks is not ideal.
 

### 2025-01-30 paper.tex
add conclusion

@@
 
+\subsection{conclusion}
+
+%本文重新审视了结合状态空间算法和自注意力算法的混合建模架构在上下文学习任务中的表现。通过详细的分析和广泛的实验，我们揭示了现有混合模型在上下文学习任务中的局限性，尽管它们在大多数语言建模任务中相比单独使用状态空间或自注意力算法表现更好。
+%我们提出的“Self-Attention before LM-Head”方法在解决这些局限性方面取得了显著进展。通过修改混合架构，使状态空间和自注意力使用相同的编码，并在语言模型头部（LM-Head）之前加入由自注意力和前馈网络组成的Transformer模块，我们有效缓解了知识路由中的偏差，并增强了模型利用状态空间和自注意力机制优势的能力。这一改进在多种任务中都取得了显著的性能提升，包括标准短文本任务、自然长文本任务和合成长文本任务，并在某些任务上达到了最先进的性能水平。
+%实验结果表明，正确整合这两种算法对于充分发挥其互补优势至关重要。重新设计的Jamba-SABLH不仅提高了模型在常见任务中短距离关联回忆的准确性，还显著增强了模型处理长文本任务的能力，显示出其强大的鲁棒性和适应性。此外，在“大海捞针”任务中，我们的方法表现出色，表明其在平衡从上下文中复制答案和预测问题实际答案的能力方面具有明显优势。
+%我们的工作为混合建模架构的改进提供了新的思路，为进一步提高模型在上下文学习任务中的性能提供了有益的启示。 
+This paper re-examines the performance of the hybrid modeling architecture combining state-space algorithms and self-attention algorithms in context learning tasks.
+Through detailed analysis and extensive experiments, we reveal the limitations of existing hybrid models in context learning tasks, although they perform better than using state-space or self-attention algorithms alone in most language modeling tasks.
+Our proposed "Self-Attention before LM-Head" method has made significant progress in addressing these limitations.
+By modifying the hybrid architecture to make the state-space and self-attention use the same encoding and adding a Transformer module composed of self-attention and feed-forward networks before the language model head (LM-Head), we effectively alleviate the bias in knowledge routing and enhance the model's ability to leverage the advantages of state-space and self-attention mechanisms.
+This improvement has achieved significant performance improvements in various tasks, including standard short text tasks, natural long text tasks, and synthetic long text tasks, and has reached the state-of-the-art performance level in some tasks.
+The experimental results show that it is crucial to correctly integrate these two algorithms to fully exploit their complementary advantages.
+The redesigned Jamba-SABLH not only improves the accuracy of the model in common tasks of short-distance associative recall but also significantly enhances the model's ability to handle long text tasks, demonstrating its robustness and adaptability.
+In addition, our method performs well in the "Needle in a Haystack" task, demonstrating its significant advantage in balancing the ability to copy answers from context and predict actual answers to questions.
+Our work provides new ideas for improving the hybrid modeling architecture and provides valuable insights for further improving the performance of the model in context learning tasks.
+
 \bibliography{paper}

### 2025-01-30 paper.tex
re compose type

--- 2025-01-30 paper.tex
@@
 % Use the following line for the initial blind version submitted for review:
-% \usepackage{icml2025}
+\usepackage{icml2025}
 
 % If accepted, instead use the following line for the camera-ready submission:
-\usepackage[accepted]{icml2025}
+% \usepackage[accepted]{icml2025}
 
@@
 \section{Background}
+
 \subsection{State-Space}
@@
 \end{equation}
+
 % 从连续时间系统的状态空间模型出发，可以通过离散化方法得到离散时间的状态更新公式,方程 (2a) 和 (2b) 代表状态空间模型的离散化形式。它们描述了在离散时间间隔内，状态向量和输出向量如何基于前一个状态和当前输入进行更新。
@@
 % 通过自注意力机制，Transformer模型能够直接捕捉序列中任意两个元素之间的关系，从而有效处理长距离依赖问题。然而，自注意力机制的二次复杂度限制了Transformer模型的计算效率，使得其在处理长序列数据时表现不佳。为了克服这一局限性，研究者们提出了许多改进方法，例如~\cite{kitaev2020reformer}提出了一种基于局部敏感哈希的自注意力机制，通过减少查询和键之间的点积计算量，从而提高了Transformer模型的计算效率。同样, 这种改进方法仍然无法完全解决Transformer模型的计算效率问题, 因此揭示自注意力机制和状态空间之间的更深层次关系, 并提出一种新的混合建模架构, 以克服这些局限性是非常重要的.
-
 Through the self-attention mechanism, the Transformer model can directly capture the relationship between any two elements in the sequence, effectively handling long-distance dependency problems.
@@
 % 混合建模架构模型是一种将状态空间和自注意力进行混合建模的模型，其目的是使模型具备与Mamba类似的效率和与Transformer类似的效果。例如，jamba~\cite{lieber2024jamba}模型是一种基于混合建模架构的通用语言模型，其基本结构为8层混合循环，每个混合循环包括7个state-space模块、1个self-attention模块和8个MLP模块。通过将状态空间和自注意力进行混合建模，jamba模型能够在大多数语言建模任务上取得更好的性能。基于混合建模架构的模型在大多数语言建模任务上的表现超越了单独使用Mamba或Transformer，但是在情景学习任务上的表现并不理想。
-
 Hybrid modeling architecture models are models that combine state-space and self-attention for hybrid modeling, with the goal of making the model have efficiency similar to Mamba and effect similar to Transformer.
@@
 
-% 对于 AFQMC 这类判断句子含义是否相同的任务, CSL这类判断关键词是否在摘要中而非从摘要提取关键词的任务, 以及 CMNLI 这类判断两个句子之间是蕴涵, 中立还是矛盾关系的任务, 它们主要依赖于在序列上选择性地提取关键信息并递归地聚合状态信息.
-因此, Jamba 和 Jamba-SABLH 在这些任务上的表现差距并不显著, 而 Jamba-SABLH 在 AFQMC 和 CSL 上略微领先的原因可能是因为它修正了一些知识路由偏差.
-在 TNEWS 这类对短句进行类别预测的任务中, 由于句子不包含或很少包含上下文信息, 因此非常依赖于预训练和微调的质量.这要求模型在预训练阶段学到的知识能够在微调阶段被正确且精确地引导, 这导致了 Jamba 在 TNEWS 上的表现远不如 Jamba-SABLH.
-与 TNEWS 相反, IFLYTEK 任务中的文本全部为长上下文, 并且其中多次出现所属应用主题的词汇.
-这构成了一个相对简单的单查询关联召回任务, 其中多次出现的单个主题词汇被选择性状态空间模型允许存储在状态中, 并成为主要影响输出的因素.
-因此, 两者在 IFLYTEK 上的表现差距不大.
-在 WSC 这类代词消歧任务中, 模型需要在代词出现后能够逆向追溯到代词之前出现的名词, 并将代词指向正确的名词.
-这属于在单查询联想回忆任务中, 额外要求了对当前语言的理解能力.
-因此, 两者在 WSC 上的表现差距在这些任务中排名第二的原因就很明显了, 两个主要因素是微调的质量差距以及 Jamba-SABLH 预测前对长期强依赖关系逐渐衰减的递归聚合信息的重新全元素关注.
-For tasks like AFQMC that judge whether sentences have the same meaning, CSL that judge whether keywords are in the abstract rather than extracting keywords from the abstract, and CMNLI that judge whether two sentences imply, are neutral, or are contradictory, they mainly rely on selectively extracting key information on the sequence and recursively aggregating state information.
-Therefore, the performance gap between Jamba and Jamba-SABLH on these tasks is not significant, and the slight lead of Jamba-SABLH on AFQMC and CSL may be due to it correcting some knowledge routing bias.
-In tasks like TNEWS that predict the category of short sentences, since the sentences do not contain or contain very little context information, they rely heavily on the quality of pre-training and fine-tuning.
-This requires that the knowledge learned by the model in the pre-training phase can be correctly and accurately guided in the fine-tuning phase, resulting in Jamba's performance on TNEWS being far worse than Jamba-SABLH.
-In contrast to TNEWS, the text in the IFLYTEK task is all long context, and the vocabulary of the application topic appears multiple times.
-This constitutes a relatively simple single-query associative recall task, where the selectively stored single topic vocabulary that appears multiple times is allowed to be stored in the state by the selective state-space model and becomes the main factor affecting the output.
-Therefore, the performance gap between the two on IFLYTEK is not significant.
-In tasks like WSC that require pronoun disambiguation, the model needs to be able to trace back to the noun that appeared before the pronoun after the pronoun appears and point the pronoun to the correct noun.
-This belongs to the additional requirement of understanding the current language in the single-query associative recall task.
-Therefore, the reason for the performance gap between the two on WSC is obvious in these tasks, the two main factors are the difference in the quality of fine-tuning and the re-attention of the recursively aggregated information that gradually decays the long-term strong dependency relationship before prediction by Jamba-SABLH.
-
 \begin{table*}[!htbp]
-   \footnotesize
    \centering
@@
 
+% 对于 AFQMC 这类判断句子含义是否相同的任务, CSL这类判断关键词是否在摘要中而非从摘要提取关键词的任务, 以及 CMNLI 这类判断两个句子之间是蕴涵, 中立还是矛盾关系的任务, 它们主要依赖于在序列上选择性地提取关键信息并递归地聚合状态信息.
+因此, Jamba 和 Jamba-SABLH 在这些任务上的表现差距并不显著, 而 Jamba-SABLH 在 AFQMC 和 CSL 上略微领先的原因可能是因为它修正了一些知识路由偏差.
+在 TNEWS 这类对短句进行类别预测的任务中, 由于句子不包含或很少包含上下文信息, 因此非常依赖于预训练和微调的质量.这要求模型在预训练阶段学到的知识能够在微调阶段被正确且精确地引导, 这导致了 Jamba 在 TNEWS 上的表现远不如 Jamba-SABLH.
+与 TNEWS 相反, IFLYTEK 任务中的文本全部为长上下文, 并且其中多次出现所属应用主题的词汇.
+这构成了一个相对简单的单查询关联召回任务, 其中多次出现的单个主题词汇被选择性状态空间模型允许存储在状态中, 并成为主要影响输出的因素.
+因此, 两者在 IFLYTEK 上的表现差距不大.
+在 WSC 这类代词消歧任务中, 模型需要在代词出现后能够逆向追溯到代词之前出现的名词, 并将代词指向正确的名词.
+这属于在单查询联想回忆任务中, 额外要求了对当前语言的理解能力.
+因此, 两者在 WSC 上的表现差距在这些任务中排名第二的原因就很明显了, 两个主要因素是微调的质量差距以及 Jamba-SABLH 预测前对长期强依赖关系逐渐衰减的递归聚合信息的重新全元素关注.
+For tasks like AFQMC that judge whether sentences have the same meaning, CSL that judge whether keywords are in the abstract rather than extracting keywords from the abstract, and CMNLI that judge whether two sentences imply, are neutral, or are contradictory, they mainly rely on selectively extracting key information on the sequence and recursively aggregating state information.
+Therefore, the performance gap between Jamba and Jamba-SABLH on these tasks is not significant, and the slight lead of Jamba-SABLH on AFQMC and CSL may be due to it correcting some knowledge routing bias.
+In tasks like TNEWS that predict the category of short sentences, since the sentences do not contain or contain very little context information, they rely heavily on the quality of pre-training and fine-tuning.
+This requires that the knowledge learned by the model in the pre-training phase can be correctly and accurately guided in the fine-tuning phase, resulting in Jamba's performance on TNEWS being far worse than Jamba-SABLH.
+In contrast to TNEWS, the text in the IFLYTEK task is all long context, and the vocabulary of the application topic appears multiple times.
+This constitutes a relatively simple single-query associative recall task, where the selectively stored single topic vocabulary that appears multiple times is allowed to be stored in the state by the selective state-space model and becomes the main factor affecting the output.
+Therefore, the performance gap between the two on IFLYTEK is not significant.
+In tasks like WSC that require pronoun disambiguation, the model needs to be able to trace back to the noun that appeared before the pronoun after the pronoun appears and point the pronoun to the correct noun.
+This belongs to the additional requirement of understanding the current language in the single-query associative recall task.
+Therefore, the reason for the performance gap between the two on WSC is obvious in these tasks, the two main factors are the difference in the quality of fine-tuning and the re-attention of the recursively aggregated information that gradually decays the long-term strong dependency relationship before prediction by Jamba-SABLH.
+
 \subsection{Associative Recall}
@@
 The two models were extended to a context length of 8192 for evaluation, and the parameter settings of the two models are shown in Table~\ref{tab:associative_recall_params}.
+
+\begin{figure*}[ht]
+   \centering
+   \includegraphics[width=\linewidth]{fig/needle-in-a-haystack.pdf}
+   \caption{
+     \textbf{Needle in a Haystack}.
+      % 不同架构的模型在 Needle in a Haystack 任务上的表现.
+我们在不同上下文长度对单独使用state-space的Mamba2~\cite{mamba2}, 单独使用self-attention的Llama3~\cite{grattafiori2024llama3herdmodels}, 使用state-space和self-attention混合算法的Jamba, 以及我们的方法Jamba-SABLH进行了评估.
+我们的方法表现出最佳性能.
+      Performance of models with different architectures on the Needle in a Haystack task.
+We evaluated Mamba2~\cite{mamba2} using state-space alone, Llama3~\cite{grattafiori2024llama3herdmodels} using self-attention alone, Jamba using a hybrid algorithm of state-space and self-attention, and our method Jamba-SABLH on different context lengths.
+Our method shows the best performance.
+      }
+   \label{fig:niah}
+\end{figure*}
 
@@
 
-\begin{figure*}[ht]
-   \centering
-   \includegraphics[width=\linewidth]{fig/needle-in-a-haystack.pdf}
-   \caption{
-     \textbf{Needle in a Haystack}.
-      % 不同架构的模型在 Needle in a Haystack 任务上的表现.
-我们在不同上下文长度对单独使用state-space的Mamba2~\cite{mamba2}, 单独使用self-attention的Llama3~\cite{grattafiori2024llama3herdmodels}, 使用state-space和self-attention混合算法的Jamba, 以及我们的方法Jamba-SABLH进行了评估.
-我们的方法表现出最佳性能.
-      Performance of models with different architectures on the Needle in a Haystack task.
-We evaluated Mamba2~\cite{mamba2} using state-space alone, Llama3~\cite{grattafiori2024llama3herdmodels} using self-attention alone, Jamba using a hybrid algorithm of state-space and self-attention, and our method Jamba-SABLH on different context lengths.
-Our method shows the best performance.
-      }
-   \label{fig:niah}
-\end{figure*}
-
 \subsection{Needle in a Haystack}
@@
 
+\section*{Impact Statement}
+
+This paper presents work whose goal is to advance the field of 
+Machine Learning. There are many potential societal consequences 
+of our work, none which we feel must be specifically highlighted here.
+
 \bibliography{paper}
 \bibliographystyle{icml2025}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% APPENDIX
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\appendix
-\onecolumn
-\section{You \emph{can} have an appendix here.}
-
-You can have as much text here as you want. The main body must be at most $8$ pages long.
-For the final version, one more page can be added.
-If you want, you can use an appendix like this one.
-
-The $\mathtt{\backslash onecolumn}$ command above can be kept in place if you prefer a one-column appendix, or can be removed if you prefer a two-column appendix.
-Apart from this possible change, the style (font size, spacing, margins, page numbering, etc.) should be kept the same as the main body.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2025-01-30 paper.tex
re compose type

--- 2025-01-30 paper.tex
@@
 
-\subsection{conclusion}
+\section{conclusion}
 
